### 2016-11-21 tafaseer_group/results/Paper.Rmd
First lines.

---
# Hey Gang! This is an RNotebook intended to be used with RStudio an'it be fly stuff!
# ====================================================================================
# For documentation, check out these links:
# - https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf
# - http://rmarkdown.rstudio.com/r_notebooks.html (a bit more explanatory)
# - http://rmarkdown.rstudio.com/lesson-1.html (RNotebook is a superset of RMarkdown)
# - https://blog.rstudio.org/2016/10/05/r-notebooks/ (some advanced examples)
# - https://rmflight.github.io/posts/2012/10/papersinRmd.html (comment by a scientist-user)

title: An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
  Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
author: "F. Blunck, S. Bukhari, T. D. Keppen, J. R. Schmid"
output:
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
  html_document:
    toc: yes

# ====================================================================================
# Title (above) and outline (below) are just a first draft, please burn and rearrange!
---

# 1 The corpus

## 1.1 Data origin and possible intentions behind its compilation

## 1.2 Data extraction and transformation into processable outer form

Yo, extraction was simple like tha':

```{ruby}
#!/usr/bin/env ruby

files = [1, 2, 3]

files.each do |f|
  # This is actual code and is actually run
  # when compiling the document, so I can't
  # write things that'll break it.
  puts "#{f}: f.download_it_from_the_internets"
  puts "#{f}: f.do_cool_stuff_to_it"
  puts "#{f}: f.save_as_csv"
end
```

## 1.3 Authors of the 18 works

### 1.3.1  d. 728: Jarir ibn Atiyah (Yamamah, Damascus)

Dude's our oldest homie, 'n he swag man! Like, dude's not only a *mufassir*, naw, he actually a real poet, too, 'n know how to do some satire, ain't that cool?

### 1.3.2  d. 925: Muhammad ibn Zakariya al-Razi (Rey)
### 1.3.3  d. 923: Al-Tabari (Amol-Baghdad)
### 1.3.4  d. 971: Abū Ja'far al-Khāzin (Iran?)
### 1.3.5  d. 1044: Al-Baghawi (?)
### 1.3.6  d. 1058: Al-Mawardi (Basrah-Baghdad)
### 1.3.7  d. 1142: Abu Hafs Umar an-Nasafi (Nakhshab-Samarqand)
### 1.3.8  d. 1144: Al-Zamakhshari (Kwharezm-Mecca-Khwarezm)
### 1.3.9  d. 1201: Ibn al-Jawzi (Baghdad)
### 1.3.10 d. 1261: Ibn 'Abd as-Salam (Damascus-Egypt)
### 1.3.11 d. 1273: Al-Qurtubi (Cortoba)
### 1.3.12 d. 1286: Al-Baydawi (Shiraz-Tabriz)
### 1.3.13 d. 1310: Shams al-Dīn al-Samarqandī (Samarqand)
### 1.3.14 d. 1401: Ibn Arafa (Tunis)
### 1.3.15 d. 1414: Fairuzabadi (Fars-Mekka)
### 1.3.16 d. 1505: Al-Suyuti (Cairo)
### 1.3.17 d. 1344: Abu Hayyan al-Gharnati (Spain-Cairo)
### 1.3.18 d. 1373: Ibn Kathir (Bosra-Damascus)

# 1.4 Conventional categorisation and inter-relationships of the authors

# 2 Analysis

# 2.1 Most frequent words (MFW), Zipf's law

# 2.2 Stylometrics

# 2.3 Topic Modelling results

# 2.4 Congruences of observations with conventional views

# 2.5 Notable differences to conventional views

# 3 Conclusion

# 3.1 Possible theses based on findings

Ibn Tayymiyya was an important guy and we think we can actually prove this because the topics he writes about were present in Topic Modelling blah blah yadda yadda which is consisent with both MFW and Stylometric analyses blah blah it would be really great if something like this could be here but I really don't think so and nothing matters anyways since I'm kinda tired blah blah. In any case, all the Islamists must, after having read our awesome paper, surrender to the tenacity and ferociousness and whatnot of our findings and concede completely and immediately that, yes, without further theological considerations necessary, *ǧihād* must be the striving for peace and *islām* is the way towards universal love, and hopefully, universal income as well. At least I've succeeded in producing a block of text so that you can see what that looks like. Hipp hipp hooraaay!

# 3.2 Discussion of necessary further work

# 4 Bibliography

### 2016-11-21 tafaseer_group/altafsir_com/convert.rb
Version which produced the latest data files.

@@ -54,7 +54,7 @@ class AlTafsirYAMLFiles
     walk_tree__by_book(formats)
   end
 
-  def cts_csv_writeline(madhab, tafseer, line_no, opts = {arabic_only: false})
+  def cts_csv_writeline(madhab, tafseer, line_no, opts = {nospecialchars: false})
     # @hash contents example:
     #
     # {"position_sura"=>1,
@@ -79,20 +79,18 @@ class AlTafsirYAMLFiles
     return if (author.empty? || book.empty?)
     urn = "urn:cts:arabLit:tafsir.#{author}.#{book}:#{sura}.#{aaya}.#{line_no}"
     outname = "%03d-%03d.csv" % [madhab, tafseer]
-    if opts[:arabic_only]
-      outpath = File.join(@outpath, 'csv', 'cts+aaya_nospecialchars')
-    else
-      outpath = File.join(@outpath, 'csv', 'cts+aaya')
+    optname = (opts.map {|k,v| k if v}).compact.join(',')
+    outpath = File.join(@outpath, 'csv', ['cts+aaya', optname].reject {|i| i.empty?}.join('_'))
+    text = @hash['text']
+    if opts[:nospecialchars]
+      text = text.gsub(/[^ \p{Arabic}]/, '') # This is a *very* crude method which does not even match vowelisation!
+      text = text.squeeze
     end
+    values = [urn, text, @hash['aaya']]
     outfile = File.join(outpath, outname)
     FileUtils.mkdir_p(outpath)
     write_header = !(File.file?(outfile))
     header = ['urn', 'text', 'aaya']
-    if opts[:arabic_only]
-      values = [urn, @hash['text'].match(/[\h\p{Arabic}]/).gsub(/\s\s+/, ' '), @hash['aaya']]
-    else
-      values = [urn, @hash['text'], @hash['aaya']]
-    end
     CSV.open(outfile, 'ab') do |csv|
       if write_header
         csv << header
@@ -108,11 +106,11 @@ class AlTafsirYAMLFiles
   end
 
   def html5_write_unless_exists(madhab, tafseer)
-    print 'html5 '
     outname = "%03d-%03d.html" % [madhab, tafseer]
     outpath = File.join(@outpath, 'html5')
     outfile = File.join(outpath, outname)
     unless File.file?(outfile)
+      print 'html5 '
       FileUtils.mkdir_p(outpath)
       File.write(outfile, @header+@html+@footer)
     end
[…]

### 2016-11-22 newspaper_group/code/PersianTM2.r
complete archives

@@ -140,24 +140,24 @@ parsing <- function(x){
 }
 
 # Read corpus
+# 
+# # base_corpus <- read.table("sanai.csv", sep="\t", header=FALSE)
+# first_corpus <- read.table("sanai.csv", sep="\t", header=FALSE)
+# second_corpus <- read.table("anvari.csv", sep="\t", header=FALSE)
+# third_corpus <- read.table("attar.csv", sep="\t", header=FALSE)
+# fourth_corpus <- read.table("khaghani.csv", sep="\t", header=FALSE)
+# 
+# output_names <- c(as.character(first_corpus[,1]),
+#                   as.character(second_corpus[,1]),
+#                   as.character(third_corpus[,1]),
+#                   as.character(fourth_corpus[,1]))
+# 
+# research_corpus <- c(as.character(first_corpus[,7]),
+#                      as.character(second_corpus[,7]),
+#                      as.character(third_corpus[,7]),
+#                      as.character(fourth_corpus[,7]))
 
-# base_corpus <- read.table("sanai.csv", sep="\t", header=FALSE)
-first_corpus <- read.table("sanai.csv", sep="\t", header=FALSE)
-second_corpus <- read.table("anvari.csv", sep="\t", header=FALSE)
-third_corpus <- read.table("attar.csv", sep="\t", header=FALSE)
-fourth_corpus <- read.table("khaghani.csv", sep="\t", header=FALSE)
-
-output_names <- c(as.character(first_corpus[,1]),
-                  as.character(second_corpus[,1]),
-                  as.character(third_corpus[,1]),
-                  as.character(fourth_corpus[,1]))
-
-research_corpus <- c(as.character(first_corpus[,7]),
-                     as.character(second_corpus[,7]),
-                     as.character(third_corpus[,7]),
-                     as.character(fourth_corpus[,7]))
-
- base_corpus <- read.table("/home/tobias/Dokumente/2011_01_01-2012_12_11.csv", sep=",", header=FALSE,encoding = "UTF-8")
+ base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reducedfiles/ahram.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
 
 research_corpus <- as.character(base_corpus$V2)
  output_names <- as.character(base_corpus$V1)
[…]

### 2016-11-22 newspaper_group/code/ahramScraping.R

@@ -5,13 +5,16 @@
 
 rm(list=ls())
 #setwd("~/Dokumente/islamicate2.0/hw/newspaper_group/Aharam/2013/") # setting working directory
-
+setwd("/home/tobias/Downloads/ahram/")
 libs<-c("rvest","stringr","tidyr","methods","beepr")
 for(i in 1:length(libs)){
   suppressPackageStartupMessages(library(libs[i], character.only = TRUE))
 }
 
-source("basic_functions.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/scrapeR.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/basic_functions.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/cleanR.R")
+
 ######################################################################################################
 #                                           NOTES
 ######################################################################################################
@@ -52,8 +55,8 @@ option_list = list(
 ## if you're just starting the script
 ## this might be a better to read:
 ## the function is called per day.
-#days.to.observe.v<-generateTimeSequence("2012-12-11","2016-10-31")
-#sapply(days.to.observe.v, scrapeAhramDay)
+days.to.observe.v<-generateTimeSequence("2010-12-1","2010-12-31")
+sapply(days.to.observe.v, scrape.day.ahram)
 #sapply(days.to.observe.v, scrapeRaw)
 
 
@@ -61,9 +64,9 @@ option_list = list(
 ## with bash-script
 #scrape.day.ahram(o$day)# causes an error.
 
-#scrape.day.ahram("2013/1/1")
-scrape.day.ahram(o$day)
+#scrape.day.ahram("2010/12/1")
+#scrape.day.ahram(o$day)
 
-
-#clean.ahram(dirname = "raw_2012_12_12-2016_10_31")
+dirname<-"/home/tobias/Downloads/ahram"
+clean.ahram(dirname )
 

### 2016-11-22 newspaper_group/code/almasryalyoum.R

@@ -7,6 +7,6 @@ for(i in 1:length(libs)){
 source("scrapeR.R")
 source("cleanR.R")
 
-source.folder<-"/home/tobias/Downloads/almasryalyoum/2011"
+source.folder<-"/home/tobias/Downloads/almasryalyoum/2010"
 clean.almasryalyoum(source.folder)
 

### 2016-11-22 newspaper_group/code/arabicTM2.r

@@ -1,0 +1,365 @@
+## setwd, modify according to your needs
+
+
+rm(list=ls())
+## libraries needed
+
+library(tm)
+library(XML)
+library(RCurl)
+library(plyr)
+library(lda)
+library(LDAvis)
+library(compiler)
+
+## optional
+
+# library(RColorBrewer)
+# library(devtools) 
+# # install_github("ramnathv/rCharts")
+# library(rCharts)
+# library(d3heatmap)
+
+# if (!require("devtools")) install.packages("devtools")
+# devtools::install_github("rstudio/d3heatmap",dependencies=TRUE)
+
+## User settings:
+K <- 15
+G <- 5000#num.iterations 
+alpha <- 0.02
+eta <- 0.02
+seed <- 37
+terms_shown <- 40
+
+ language <- "Arabic" # (Persian, Arabic, Latin)
+
+
+## read in some stopwords:
+
+stop_words<-scan(file="/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/stopwords_ar.txt",what = "", sep="\n",encoding = "UTF-8")
+
+# Enable JIT-compiling
+
+enableJIT(3)
+
+
+
+ base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced_stem/ahram_stem.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
+
+research_corpus <- as.character(base_corpus$V2)
+ output_names <- as.character(base_corpus$V1)
+
+ 
+research_corpus <- gsub("[[:punct:]]", " ", research_corpus)  # replace punctuation with space
+research_corpus <- gsub("[[:cntrl:]]", " ", research_corpus)  # replace control characters with space
+research_corpus <- gsub("^[[:space:]]+", "", research_corpus) # remove whitespace at beginning of documents
+research_corpus <- gsub("[[:space:]]+$", "", research_corpus) # remove whitespace at end of documents
+research_corpus <- gsub("[0-9]", "", research_corpus) #remove numbers
+
+
+# tokenize on space and output as a list:
+doc.list <- strsplit(research_corpus, "[[:space:]]+")
+
+# produce dictionary for stemming:
+
+
+
+
+all_words <- unlist(doc.list)
+#out<-stem(all_words, transliteration = TRUE, returnStemList = TRUE)
+#str(out)
+
+all_words<-all_words[all_words!=""]
+corpus_words <- unique(all_words)
+corpus_words <- sort(corpus_words)
+
+
[…]

### 2016-11-22 newspaper_group/code/cleanR.R

@@ -38,7 +38,7 @@ clean.almasryalyoum <- function(source.folder){
       
       
       ## since all homepages look the same I can skip the if-statements (cf. al-watan.R)
-      write.table(data.frame(i,sub("\"","",text.c),gsub("\"","",title.c)),col.names = FALSE,row.names = FALSE,paste(source.folder,".csv",sep=""),sep = ",",fileEncoding = "UTF-8",append = T)
+      write.table(data.frame(i,sub("\"","",text.c),gsub("\"","",title.c)),col.names = FALSE,row.names = FALSE,paste(source.folder,".csv",sep=""),sep = ",",quote = "",fileEncoding = "UTF-8",append = T)
       i<-i+1
     },error =function(e){write(paste("page",my.filename,"could not be loaded",sep=" "),"log",append = TRUE )})
     
@@ -53,9 +53,10 @@ clean.almasryalyoum <- function(source.folder){
 ##                              AHRAM
 ###############################################################################
 
-clean.ahram<- function(){
-  my.filename<-paste(dirname,".csv",sep = "")
+clean.ahram<- function(dirname){
   
+  my.filename<-paste(dirname,".csv",sep = "")
+  print(my.filename)
   for(my.file in dir(dirname,pattern = "*.aspx")){
     
     tryCatch({

### 2016-11-22 newspaper_group/code/scrapeR.R

@@ -101,36 +101,39 @@ scrape.day.thawra<- function(day.homepage.url){
 ###############################################################################
 
 scrape.day.ahram<- function(day.to.observe){
-  target.folder<- "~/Dokumente/islamicate2.0/hw/corpora/newspaper_archive/Aharam/2013"
+  target.folder<- "~/Downloads/ahram"
   base.ahram.url<- "http://www.ahram.org.eg/archive/"
   ahram.url<-"http://www.ahram.org.eg/archive/news/" # articles are saved one stage down. 
   
   ahram.day.url<-paste(ahram.url,day.to.observe,"/index.aspx",sep="")
-  
+
   homepages.rel.v<-getLinks(ahram.day.url,"a")
+
   homepages.v<-filter_homepages.ahram(homepages.rel.v)# also prepends http
-  
+
   homepages.v<-homepages.v[grep("*[0-9].aspx$", homepages.v)]# i'm only interested in the articles
-  
-  homepages.rel.v<- gsub("/", "_", homepages.rel.v)
+  print(homepages.v)
+  homepages.names.v<- gsub("/", "_", homepages.v)
   for(i in 1:length(homepages.v)){
     
     # to avoid the duplicate issue. also resulting in http:__ (not very relevant)
-    my.filename <- paste(target.folder, gsub("/", "_", homepages.rel.v[i]), sep = "/")
-    print(my.filename)
-    if(!file.exists(my.filename)){
-      
-      tryCatch({
-        ahram.homepage<-read_html(homepages.v[i],encoding = "UTF-8")
-        write_xml(ahram.homepage,my.filename)
-        
-        sleep(0.1)}
-        ,error = function(e){
-          write(homepages.v[i],paste(target.folder,'log',sep=""),append = TRUE)
-        })
-      
-    }# end of file.exists
-    else{print(paste("skip",homepages.v[i],"because i have it already.",sep=" "))}
+    my.filename <- paste(target.folder, gsub("/", "_", homepages.names.v[i]), sep = "/")
+    #print(my.filename)
+     if(!file.exists(my.filename)){
+    # 
+       tryCatch({
+         ahram.homepage<-read_html(homepages.v[i],encoding = "UTF-8")
+         write_xml(ahram.homepage,my.filename)
+    # 
+         sleep(0.1)}
+         ,error = function(e){
+           print("something went wrong while downloading.")
+    #       #write(homepages.v[i],paste(target.folder,'/log',sep=""),append = TRUE)
[…]

### 2016-11-22 newspaper_group/code/scrape_session.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-start="2015/1/1"
+start="2010/1/1"
 
 
 
@@ -8,14 +8,14 @@ session=scraper_session
 tmux new-session -d -s $session || exit    
 
 
-days=$(seq 0 30 | xargs -I {} date -d "$start {} day" +%Y/%-m/%-d)
+days=$(seq 0 31 | xargs -I {} date -d "$start {} day" +%Y/%-m/%-d)
 	   
 # achtung leerzeichen!
 i=0;
 for day in $days; do
        i=$((i+1))       
-#       tmux new-window -t $session:$i -n '' "Rscript ahramScraping.R --day=$day"
-       tmux new-window -t $session:$i -n '' "Rscript hespress.R --day=$day"
+       tmux new-window -t $session:$i -n '' "Rscript ahramScraping.R --day=$day"
+#       tmux new-window -t $session:$i -n '' "Rscript hespress.R --day=$day"
 done
 
 

### 2016-11-22 newspaper_group/code/tests.R

@@ -9,56 +9,160 @@ month.names<-format(month.dates, "%B")
 
 
 ####
-corpus2011<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
-corpus2010<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+# corpus2011<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+# corpus2010<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+# 
+# 
+# 
+#   dec<-corpus2010$V4[which(corpus2010$V2==month.names[12])]
+# 
+#   jan<-corpus2011$V4[which(corpus2011$V2==month.names[1])]
+#   feb<-corpus2011$V4[which(corpus2011$V2==month.names[2])]
+#   mar<-corpus2011$V4[which(corpus2011$V2==month.names[3])]
+#   apr<-corpus2011$V4[which(corpus2011$V2==month.names[4])]
+#   may<-corpus2011$V4[which(corpus2011$V2==month.names[5])]
+#   text.v<-c(dec,jan,feb,mar,apr,may)
+# 
+#   ids <- 1: length(text.v)
+# 
+#   newCorpus<-data.frame(ids,text.v,stringsAsFactors = F)
+# 
+# 
+# write.table(newCorpus,col.names = FALSE,row.names = FALSE,"/home/tobias/Dropbox/Dokumente/islamicate2.0/reducedfiles/hespress.csv",sep = ",",fileEncoding = "UTF-8",append = F)
+# 
+# 
+# 
+# 
+# 
+# corpus2011<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Thawra/thawra2010_11.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+# 
+# 
[…]

### 2016-11-22 newspaper_group/code/text_analysisJM.R

@@ -24,33 +24,34 @@ library(wordcloud)
 
 ### an alternative way to load data
 ## you have to set header=FALSE
-filename<-"/home/tobias/Dropbox/Dokumente/islamicate2.0/AlWatan/alwatan.csv"##"alwatan2011.500lines.csv"
+filename<-"/home/tobias/Dropbox/Dokumente/islamicate2.0/reducedfiles/alwatan_stem_tr.csv"
+base_corpus <- read.table(filename, sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
+
 data <- read.csv(filename, encoding = "UTF-8",sep = ",",header = FALSE,stringsAsFactors=F)
 
 ### some additional cleaning.
 
-data[,4] <- gsub("[[:punct:]]", " ", data[,4])  # replace punctuation with space
-data[,4] <- gsub("[[:cntrl:]]", " ", data[,4])  # replace control characters with space
-data[,4] <- gsub("^[[:space:]]+", "", data[,4]) # remove whitespace at beginning of documents
-data[,4] <- gsub("[[:space:]]+$", "", data[,4]) # remove whitespace at end of documents
-data[,4] <- gsub("[0-9]", "", data[,4]) #remove numbers
-data[,4]<- gsub("[:alpha:]","", data[,4])
+data[,2] <- gsub("[[:punct:]]", " ", data[,2])  # replace punctuation with space
+# data[,2] <- gsub("[[:cntrl:]]", " ", data[,2])  # replace control characters with space
+# data[,2] <- gsub("^[[:space:]]+", "", data[,2]) # remove whitespace at beginning of documents
+# data[,2] <- gsub("[[:space:]]+$", "", data[,2]) # remove whitespace at end of documents
+# data[,2] <- gsub("[0-9]", "", data[,2]) #remove numbers
+# data[,2]<- gsub("[:alpha:]","", data[,2])
 
-my.input.data<-data.frame(data[,4],stringsAsFactors = F)
+my.input.data<-data.frame(data[,2],stringsAsFactors = F)
 
-
-
-stop.words<-scan(file="/home/tobias/Downloads/stopwords_ar.txt",what = "", sep="\n",encoding = "UTF-8")
+stop_words<-scan(file="/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/stopwords_ar_tr.txt",what = "", sep="\n",encoding = "UTF-8")
[…]

### 2016-11-23 tafaseer_group/analysis/topicmodel.R
Add some comments

@@ -1,14 +1,9 @@
 library(tm)
-
 library(topicmodels)
 
-filenames <- dir()
-
+filenames <- dir() # TODO: ask thom where he had this running? the txt folder?
 files <- lapply(filenames,readLines)
-
 docs <- Corpus(VectorSource(files))
-
-
 
 #Create document-term matrix-Takes awhile
 dtm <- DocumentTermMatrix(docs)
@@ -22,16 +17,16 @@ length(freq)
 ord <- order(freq,decreasing=TRUE)
 #List all terms in decreasing order of freq and write to disk
 freq[ord]
-write.csv(freq[ord], "word_freq.csv”)
+write.csv(freq[ord], "word_freq.csv")
 
+#parameters
 burnin <- 4000
 iter <- 2000
 thin <- 500
 seed <-list(2003,5,63,100001,765)
 nstart <- 5
 best <- TRUE
-
-k <- 18
+k <- 18 # number of works
 
 ldaOut <-LDA(dtm,k, method= "Gibbs" , control=list(nstart=nstart, seed = seed, best=best, burnin = burnin, iter = iter, thin=thin))
 
@@ -59,5 +54,3 @@ sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
 #write to file
 write.csv(topic1ToTopic2,file=paste("LDAGibbs",k,"Topic1ToTopic2.csv"))
 write.csv(topic2ToTopic3,file=paste("LDAGibbs",k,"Topic2ToTopic3.csv"))
-
-

### 2016-11-24 tafaseer_group/results/Paper.Rmd
Adding Maryam to list of authors (sooorrryyyyy!!!!)
Changes to script

@@
 ---
-# Hey Gang! This is an RNotebook intended to be used with RStudio an'it be fly stuff!
-# ====================================================================================
-# For documentation, check out these links:
-# - https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf
-# - http://rmarkdown.rstudio.com/r_notebooks.html (a bit more explanatory)
-# - http://rmarkdown.rstudio.com/lesson-1.html (RNotebook is a superset of RMarkdown)
-# - https://blog.rstudio.org/2016/10/05/r-notebooks/ (some advanced examples)
-# - https://rmflight.github.io/posts/2012/10/papersinRmd.html (comment by a scientist-user)
-
 title: An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
   Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
-author: "F. Blunck, S. Bukhari, T. D. Keppen, J. R. Schmid"
+author: "F. Blunck, S. Bukhari, M. Foradi, T. D. Keppen, J. R. Schmid"
 output:
-  pdf_document:
+  html_document:
     toc: yes
@@
     toc: yes
-  html_document:
+  pdf_document:
     toc: yes
-
-# ====================================================================================
-# Title (above) and outline (below) are just a first draft, please burn and rearrange!
 ---
@@
 
-Yo, extraction was simple like tha':
+Yo, extraction was simple like tha' أخي:
 
-```{ruby}
-#!/usr/bin/env ruby
-
-files = [1, 2, 3]
-
-files.each do |f|
-  # This is actual code and is actually run
-  # when compiling the document, so I can't
-  # write things that'll break it.
-  puts "#{f}: f.download_it_from_the_internets"
-  puts "#{f}: f.do_cool_stuff_to_it"
-  puts "#{f}: f.save_as_csv"
-end
+```{R}
+print(paste('Hello', 'world', '!'))
 ```

### 2016-11-24 tafaseer_group/retrieval/convert.rb
Adding code to write corpus into sqlite3 database

@@ -6,9 +6,35 @@ require 'pandoc-ruby'
 require 'fileutils'
 require 'sanitize'
 require 'pp'
+require 'sqlite3'
+require 'active_record'
+require 'awesome_print'
+require 'pry'
 require_relative 'lib/asciiarabic'
 require_relative 'lib/flat_hash'
 require_relative 'lib/numeric_to_hindi'
+
+ActiveRecord::Base.establish_connection(
+  adapter: 'sqlite3',
+  database: '../../corpora/altafsir_com/processed/corpus.sqlite3'
+)
+
+class CTSUnit < ActiveRecord::Base
+  # CREATE TABLE units(
+  #   id          INTEGER PRIMARY KEY AUTOINCREMENT NOT NULL, 
+  #   cts_urn     CHAR(255) NOT NULL, 
+  #   text        TEXT, 
+  #   label       TEXT, 
+  #   title       CHAR(255), 
+  #   author_name CHAR(255), 
+  #   author_era  INTEGER
+  #   category_id INTEGER NOT NULL, 
+  #   author_id   INTEGER NOT NULL, 
+  #   sura_id     INTEGER NOT NULL,
+  #   aaya_id     NOT NULL, 
+  # );
+  default_scope {order('id ASC')}
+end
 
 class AlTafsirYAMLFiles
   def initialize
@@ -54,6 +80,26 @@ class AlTafsirYAMLFiles
     walk_tree__by_book(formats)
   end
 
+  def remove_specialchars(text)
+    text = text.gsub(/[^ \p{Arabic}]/, '') # This is a *very* crude method which does not even match vowelisation!
+    return text.squeeze
+  end
+
+  def urn(line_no)
+    # CITE CTS URN example:
+    # urn:cts:arabLit:tafsir.author.work:1.2.1234
+    author = ASCIIArabic.translit(@hash['meta_author'])
+    book   = ASCIIArabic.translit(@hash['meta_title'])
+    sura   = @hash['position_sura'].to_i
+    aaya   = @hash['position_aaya'].to_i
+    # No need to continue if we don't have the full URN
+    if (author.empty? || book.empty?)
+      return false
+    else
+      return "urn:cts:arabLit:tafsir.#{author}.#{book}:#{sura}.#{aaya}.#{line_no}"
+    end
+  end
+
   def cts_csv_writeline(madhab, tafseer, line_no, opts = {nospecialchars: false})
     # @hash contents example:
     #
@@ -67,25 +113,12 @@ class AlTafsirYAMLFiles
[…]

### 2016-11-24 newspaper_group/code/tests.R
storing the raw files on my computer...

@@ -3,109 +3,170 @@ rm(list=ls())
 
 
 # might be nec. to change this.
-Sys.setlocale("LC_TIME", "ar_AE.utf8");
-month.dates<-seq(as.Date("2012-01-01"), as.Date("2012-12-31"), "months")
-month.names<-format(month.dates, "%B")
-
-
-####
-# corpus2011<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
-# corpus2010<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
-# 
-# 
-# 
-#   dec<-corpus2010$V4[which(corpus2010$V2==month.names[12])]
-# 
-#   jan<-corpus2011$V4[which(corpus2011$V2==month.names[1])]
-#   feb<-corpus2011$V4[which(corpus2011$V2==month.names[2])]
-#   mar<-corpus2011$V4[which(corpus2011$V2==month.names[3])]
-#   apr<-corpus2011$V4[which(corpus2011$V2==month.names[4])]
-#   may<-corpus2011$V4[which(corpus2011$V2==month.names[5])]
-#   text.v<-c(dec,jan,feb,mar,apr,may)
-# 
-#   ids <- 1: length(text.v)
-# 
-#   newCorpus<-data.frame(ids,text.v,stringsAsFactors = F)
-# 
-# 
-# write.table(newCorpus,col.names = FALSE,row.names = FALSE,"/home/tobias/Dropbox/Dokumente/islamicate2.0/reducedfiles/hespress.csv",sep = ",",fileEncoding = "UTF-8",append = F)
-# 
-# 
-# 
-# 
-# 
-# corpus2011<-read.csv(file="/home/tobias/Dropbox/Dokumente/islamicate2.0/Thawra/thawra2010_11.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
-# 
-# 
-# 
-# 
-# dec<-corpus2011$V4[which(corpus2011$V2=12)]
-# 
-# jan<-corpus2011$V4[which(corpus2011$V2==1)]
-# feb<-corpus2011$V4[which(corpus2011$V2==2)]
[…]

### 2016-11-25 tafaseer_group/retrieval/convert.rb
Adding plain_nohadith format.

@@ -1,5 +1,6 @@
 #!/usr/bin/env ruby
 
+require 'bundler/setup'
 require 'yaml'
 require 'csv'
 require 'pandoc-ruby'
@@ -10,6 +11,7 @@ require 'sqlite3'
 require 'active_record'
 require 'awesome_print'
 require 'pry'
+require 'nokogiri'
 require_relative 'lib/asciiarabic'
 require_relative 'lib/flat_hash'
 require_relative 'lib/numeric_to_hindi'
@@ -100,6 +102,11 @@ class AlTafsirYAMLFiles
     end
   end
 
+  # For purposes of the DH Leipzig/Maryland/etc. research groups (be
+  # able to use To Pan, etc.) the CSV files must comply with CITE CTS.
+  # The specs are at
+  # http://cite-architecture.github.io/ctsurn_spec/specification.html.
+  
   def cts_csv_writeline(madhab, tafseer, line_no, opts = {nospecialchars: false})
     # @hash contents example:
     #
@@ -166,20 +173,27 @@ class AlTafsirYAMLFiles
     outfile
   end
 
-  def plain_text_write(html_file, madhab, tafseer)
+  def plain_text_write(html_file, madhab, tafseer, opts = {nohadith: false})
     outname = "%03d-%03d.txt" % [madhab, tafseer]
-    outpath = File.join(@outpath, 'plain')
+    lastdir = "complete"
+    html = Nokogiri::HTML(File.read(html_file))
+    if opts[:nohadith]
+      lastdir = "nohadith"
+      html.at_css('p.hadith').remove
+    end
+    html = html.at_css('body').text.strip
+    outpath = File.join(@outpath, 'plain', lastdir)
     plain_file = File.join(outpath, outname)
     FileUtils.mkdir_p(outpath)
     File.open(plain_file, 'w') do |outfile|
       print 'plain '
-        outfile.puts Sanitize.fragment(@html, {
-          whitespace_elements: {
-            'h1':      { before: "\n",   after: "\n\n" },
-            'h2':      { before: "\n",   after: "\n"   },
-            'section': { before: "\n\n", after: "\n"   },
-            'p':       { before: "\n",   after: "\n"   }
-        }})
+      outfile.puts Sanitize.fragment(html, {
+        whitespace_elements: {
+          'h1':      { before: "\n",   after: "\n\n" },
+          'h2':      { before: "\n",   after: "\n"   },
+          'section': { before: "\n\n", after: "\n"   },
[…]

### 2016-11-25 tafaseer_group/analysis/charcount_quran_75-23.sh
Moving data files (input and output both) to their own subfolder. Adapting scripts.

@@ -7,8 +7,10 @@ QUERY1="SELECT category_id, author_id, sum(length(text)) FROM cts_units WHERE su
 QUERY2="SELECT category_id, author_id, sum(length(text)) FROM cts_units GROUP BY category_id, author_id;"
 
 DB_FILE="../../corpora/altafsir_com/processed/corpus.sqlite3"
+OUT_FILE="data_IO/charcount_quran_75-23.txt"
 
-echo "Character counts for $SURA:$AAYA..."
-echo $QUERY1 | sqlite3 $DB_FILE
-echo "Character counts for all the text..."
-echo $QUERY2 | sqlite3 $DB_FILE
+echo "Writing into $OUT_FILE:"
+echo "  character counts for $SURA:$AAYA..."
+echo $QUERY1 | sqlite3 $DB_FILE > $OUT_FILE
+echo "  character counts for all the text..."
+echo $QUERY2 | sqlite3 $DB_FILE > $OUT_FILE

### 2016-11-25 tafaseer_group/analysis/create_top200mfw.rb

@@ -2,11 +2,12 @@
 
 require 'csv'
 
-mfw_list_dir = '/home/jrs/ba/analysis/output'
-stopwords = CSV.read('stopwords.csv').flatten
+mfw_list_dir = '/home/jrs/ba/analysis/output' # TODO: bring into hw!!!
+stopwords = CSV.read(File.join('data_IO', 'stopwords.csv')).flatten
+output = File.join('data_IO', "top#{n_max}mfw.csv")
 n_max=200
 
-CSV.open("top#{n_max}mfw.csv", 'w') do |csv|
+CSV.open(output, 'w') do |csv|
   files = Dir.glob(mfw_list_dir + '/wordcount-???-???.csv')
   header = ['pos']
   files.each do |f|

### 2016-11-25 tafaseer_group/analysis/topicmodel.R
Changing Matt's/Thom's topicmodel script to be easier to read and understand.

@@ -1,56 +1,113 @@
-library(tm)
-library(topicmodels)
+#!/usr/bin/env Rscript
 
-filenames <- dir('../../corpora/altafsir_com/processed/plain/')
-files <- lapply(filenames, readLines)
-docs <- Corpus(VectorSource(files))
+params = list(
+  burnin  = 4000,
+  iter    = 2000,
+  thin    =  500,
+  seed    = list(2003, 5, 63, 100001, 765),
+  nstart  =    5,
+  best    = TRUE,
+  # k     =   18, # Number of works
+  k       =    2, # For testing purposes only
+  verbose = 2000  # Show progress every x iterations
+)
 
-#Create document-term matrix-Takes awhile
-dtm <- DocumentTermMatrix(docs)
-#convert rownames to filenames
-rownames(dtm) <- filenames
-#collapse matrix by summing over columns
-freq <- colSums(as.matrix(dtm))
-#length should be total number of terms
-length(freq)
-#create sort order (descending)
-ord <- order(freq,decreasing=TRUE)
-#List all terms in decreasing order of freq and write to disk
-freq[ord]
-write.csv(freq[ord], "word_freq.csv")
+build_dtm <- function(file)
+{
+  message('Reading in files...')
+  file = lapply(file, readLines)
+  message('Building corpus...')
+  corpus = Corpus(VectorSource(file))
+  message('Building DT matrix...')
+  DocumentTermMatrix(corpus)
+}
 
-#parameters
-burnin <- 4000
-iter <- 2000
-thin <- 500
-seed <-list(2003,5,63,100001,765)
-nstart <- 5
-best <- TRUE
-k <- 18 # number of works
+crunch_lda <- function(dtm, params)
+{
+  message('Crunching LDA function...')
+  LDA(
+    dtm,
+    params$k,
+    method='Gibbs', # Who is he and why do we like him?
+    control=params
+  )
+}
 
-ldaOut <-LDA(dtm,k, method= "Gibbs" , control=list(nstart=nstart, seed = seed, best=best, burnin = burnin, iter = iter, thin=thin))
+write_topics <- function(src, lda, k)
+{
+  message('Building topics from LDA results...')
+  topics = as.matrix(topics(lda))
+  write.csv(
+    topics, 
[…]

### 2016-11-25 tafaseer_group/analysis/topicmodel.R
Changing k back to 18

@@ -7,8 +7,8 @@ params = list(
   seed    = list(2003, 5, 63, 100001, 765),
   nstart  =    5,
   best    = TRUE,
-  # k     =   18, # Number of works
-  k       =    2, # For testing purposes only
+  k       =   18, # Number of works
+  # k     =    2, # For testing purposes only
   verbose = 2000  # Show progress every x iterations
 )
 

### 2016-11-25 tafaseer_group/retrieval/convert.rb
Adding generation of hadith-free plain text representation.

@@ -175,25 +175,29 @@ class AlTafsirYAMLFiles
 
   def plain_text_write(html_file, madhab, tafseer, opts = {nohadith: false})
     outname = "%03d-%03d.txt" % [madhab, tafseer]
-    lastdir = "complete"
-    html = Nokogiri::HTML(File.read(html_file))
-    if opts[:nohadith]
-      lastdir = "nohadith"
-      html.at_css('p.hadith').remove
-    end
-    html = html.at_css('body').text.strip
+    lastdir = opts[:nohadith] ? 'nohadith' : 'complete'
     outpath = File.join(@outpath, 'plain', lastdir)
     plain_file = File.join(outpath, outname)
-    FileUtils.mkdir_p(outpath)
-    File.open(plain_file, 'w') do |outfile|
-      print 'plain '
-      outfile.puts Sanitize.fragment(html, {
-        whitespace_elements: {
-          'h1':      { before: "\n",   after: "\n\n" },
-          'h2':      { before: "\n",   after: "\n"   },
-          'section': { before: "\n\n", after: "\n"   },
-          'p':       { before: "\n",   after: "\n"   }
-      }})
+    unless File.exist?(plain_file)
+      html = Nokogiri::HTML(File.read(html_file))
+      if opts[:nohadith]
+        print 'plain_nohadith '
+        hadith_paragraphs = html.at_css('p.hadith')
+        hadith_paragraphs.remove if hadith_paragraphs
+      else
+        print 'plain '
+      end
+      html = html.at_css('body').text.strip
+      FileUtils.mkdir_p(outpath)
+      File.open(plain_file, 'w') do |outfile|
+        outfile.puts Sanitize.fragment(html, {
+          whitespace_elements: {
+            'h1':      { before: "\n",   after: "\n\n" },
+            'h2':      { before: "\n",   after: "\n"   },
+            'section': { before: "\n\n", after: "\n"   },
+            'p':       { before: "\n",   after: "\n"   }
+        }})
+      end
     end
   end
 
@@ -255,7 +259,6 @@ class AlTafsirYAMLFiles
         plain_text_write(html_file, m, t, nohadith: true) if @formats[:plain_nohadith]
         other_formats_write(html_file, m, t, formats) if @formats[:other]
         puts "(%s files, %ss)" % [i, (Time.now-t0).round(1)]
-        exit
       end # tafaseer
     end # madahib
   end

### 2016-11-25 newspaper_group/code/scrape_session.sh
created resources folder but with full name to prevent confusion

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+start="2015/1/1"
+
+
+
+session=scraper_session
+tmux new-session -d -s $session || exit    
+
+
+days=$(seq 0 30 | xargs -I {} date -d "$start {} day" +%Y/%-m/%-d)
+	   
+# achtung leerzeichen!
+i=0;
+for day in $days; do
+       i=$((i+1))       
+#       tmux new-window -t $session:$i -n '' "Rscript ahramScraping.R --day=$day"
+       tmux new-window -t $session:$i -n '' "Rscript hespress.R --day=$day"
+done
+
+
+tmux attach-session -t $session
+   
+
+echo date -d "$start + $intervall day" '+%Y/%-m/%-d'
+
+# zum schluss mal einen test machen, obs auch wirlich funktioniert hat.

### 2016-11-25 schmid_jonathan/lib/cleanup.R

@@ -1,0 +1,17 @@
+# Simple but effective by way of Unicode regex group
+cleanArabicString <- function(string) {
+  return(
+    gsub(
+      # Second, collapse all occurances of multiple
+      # spaces into a single space each.
+      '[ ]{2,}', ' ', 
+      gsub(
+        # First, remove everything that is not a space 
+        # or an Arabic character or that is an opening
+        # or closing perenthesis
+        '[^( \\p{Arabic})]|[()]', '', 
+        text.single_string.v, perl = TRUE
+      ), perl = TRUE
+    )
+  )
+}

### 2016-11-25 tafaseer_group/analysis/charcount_quran_75-23.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+SURA=75
+AAYA=23
+
+QUERY1="SELECT category_id, author_id, sum(length(text)) FROM cts_units WHERE sura_id = $SURA and aaya_id = $AAYA GROUP BY category_id, author_id;"
+QUERY2="SELECT category_id, author_id, sum(length(text)) FROM cts_units GROUP BY category_id, author_id;"
+
+DB_FILE="../../corpora/altafsir_com/processed/corpus.sqlite3"
+
+echo "Character counts for $SURA:$AAYA..."
+echo $QUERY1 | sqlite3 $DB_FILE
+echo "Character counts for all the text..."
+echo $QUERY2 | sqlite3 $DB_FILE

### 2016-11-25 tafaseer_group/analysis/csv_to_rds.r

@@ -1,0 +1,7 @@
+#!/usr/bin/env Rscript
+
+library(data.table)
+
+args = commandArgs(trailingOnly = TRUE)
+csv = fread(args[1])
+saveRDS(csv, args[2])

### 2016-11-25 tafaseer_group/analysis/topicmodel.R

@@ -1,0 +1,56 @@
+library(tm)
+library(topicmodels)
+
+filenames <- dir('../../corpora/altafsir_com/processed/plain/')
+files <- lapply(filenames, readLines)
+docs <- Corpus(VectorSource(files))
+
+#Create document-term matrix-Takes awhile
+dtm <- DocumentTermMatrix(docs)
+#convert rownames to filenames
+rownames(dtm) <- filenames
+#collapse matrix by summing over columns
+freq <- colSums(as.matrix(dtm))
+#length should be total number of terms
+length(freq)
+#create sort order (descending)
+ord <- order(freq,decreasing=TRUE)
+#List all terms in decreasing order of freq and write to disk
+freq[ord]
+write.csv(freq[ord], "word_freq.csv")
+
+#parameters
+burnin <- 4000
+iter <- 2000
+thin <- 500
+seed <-list(2003,5,63,100001,765)
+nstart <- 5
+best <- TRUE
+k <- 18 # number of works
+
+ldaOut <-LDA(dtm,k, method= "Gibbs" , control=list(nstart=nstart, seed = seed, best=best, burnin = burnin, iter = iter, thin=thin))
+
+#write out results
+#docs to topics
+ldaOut.topics <- as.matrix(topics(ldaOut))
+write.csv(ldaOut.topics,file=paste("LDAGibbs", k, "DocsToTopics.csv"))
+
+#top 6 terms in each topic
+ldaOut.terms <- as.matrix(terms(ldaOut,6))
+write.csv(ldaOut.terms,file=paste("LDAGibbs",k,"TopicsToTerms.csv"))
+
+#probabilities associated with each topic assignment
+topicProbabilities <- as.data.frame(ldaOut@gamma)
+write.csv(topicProbabilities,file=paste("LDAGibbs",k,"TopicProbabilities.csv"))
+
+#Find relative importance of top 2 topics
+topic1ToTopic2 <- lapply(1:nrow(dtm),function(x)
+  sort(topicProbabilities[x,])[k]/sort(topicProbabilities[x,])[k-1])
+
+#Find relative importance of second and third most important topics
+topic2ToTopic3 <- lapply(1:nrow(dtm),function(x)
+  sort(topicProbabilities[x,])[k-1]/sort(topicProbabilities[x,])[k-2])
+
+#write to file
[…]

### 2016-11-25 tafaseer_group/retrieval/convert.rb

@@ -1,0 +1,250 @@
+#!/usr/bin/env ruby
+
+require 'yaml'
+require 'csv'
+require 'pandoc-ruby'
+require 'fileutils'
+require 'sanitize'
+require 'pp'
+require 'sqlite3'
+require 'active_record'
+require 'awesome_print'
+require 'pry'
+require_relative 'lib/asciiarabic'
+require_relative 'lib/flat_hash'
+require_relative 'lib/numeric_to_hindi'
+
+ActiveRecord::Base.establish_connection(
+  adapter: 'sqlite3',
+  database: '../../corpora/altafsir_com/processed/corpus.sqlite3'
+)
+
+class CTSUnit < ActiveRecord::Base
+  # CREATE TABLE units(
+  #   id          INTEGER PRIMARY KEY AUTOINCREMENT NOT NULL, 
+  #   cts_urn     CHAR(255) NOT NULL, 
+  #   text        TEXT, 
+  #   label       TEXT, 
+  #   title       CHAR(255), 
+  #   author_name CHAR(255), 
+  #   author_era  INTEGER
+  #   category_id INTEGER NOT NULL, 
+  #   author_id   INTEGER NOT NULL, 
+  #   sura_id     INTEGER NOT NULL,
+  #   aaya_id     NOT NULL, 
+  # );
+  default_scope {order('id ASC')}
+end
+
+class AlTafsirYAMLFiles
+  def initialize
+    @inpath  = File.join('..', '..', 'corpora', 'altafsir_com', 'processed', 'yaml')
+    @outpath = File.join('..', '..', 'corpora', 'altafsir_com', 'processed')
+    @number_of_madahib = 10
+    @number_of_suwar  = 114
+    @number_of_tafaseer_per_madhab = [8, 20, 10, 2, 7, 7, 4, 3, 5, 2]
+    @number_of_aayaat_per_sura = [
+      7, 286, 200, 176, 120, 165, 206, 75, 129, 109, 123, 111, 43, 52, 99, 128,
+      111, 110, 98, 135, 112, 78, 118, 64, 77, 227, 93, 88, 69, 60, 34, 30, 73,
+      54, 45, 83, 182, 88, 75, 85, 54, 53, 89, 59, 37, 35, 38, 29, 18, 45, 60,
[…]

### 2016-11-25 tafaseer_group/retrieval/download.r

@@ -1,0 +1,164 @@
+#!/usr/bin/env Rscript
+# Only runs on R >= 3.3.1!
+# Requires: install.packages(c('urltools', 'rvest', 'XML', 'magrittr', 'stringr', 'optparse'))
+# Remember: every line of code one liability!
+
+for (lib in c('urltools', 'curl', 'rvest', 'stringr', 'optparse', 'tools', 'methods')) {
+  suppressPackageStartupMessages(library(lib, character.only = TRUE))
+}
+
+default_url = 'http://www.altafsir.com/Tafasir.asp?tMadhNo=0&tTafsirNo=0&tSoraNo=1&tAyahNo=1&tDisplay=yes&LanguageID=1'
+parameters  = param_get(default_url, c('tMadhNo', 'tTafsirNo', 'tSoraNo', 'tAyahNo'))
+save_path   = file.path('..', '..', 'corpora', 'altafsir_com', 'downloaded')
+
+# Dropdown boxes 1 and 3
+number_of_madahib = 10
+number_of_suwar  = 114
+# Dropdown boxes 2 and 4,
+# thank you Christoph!
+number_of_tafaseer_per_madhab = c(8, 20, 10, 2, 7, 7, 4, 3, 5, 2) 
+number_of_aayaat_per_sura     = c(7, 286, 200, 176, 120, 165, 206, 75, 129, 109, 123, 111, 43, 52, 99, 128, 111, 110, 98, 135, 112, 78, 118, 64, 77, 227, 93, 88, 69, 60, 34, 30, 73, 54, 45, 83, 182, 88, 75, 85, 54, 53, 89, 59, 37, 35, 38, 29, 18, 45, 60, 49, 62, 55, 78, 96, 29, 22, 24, 13, 14, 11, 11, 18, 12, 12, 30, 52, 52, 44, 28, 28, 20, 56, 40, 31, 50, 40, 46, 42, 29, 19, 36, 25, 22, 17, 19, 26, 30, 20, 15, 21, 11, 8, 8, 19, 5, 8, 8, 11, 11, 8, 3, 9, 5, 4, 7, 3, 6, 3, 5, 4, 5, 6)
+
+download_all <- function(url, path, start_pos=c(1,1,1,1), stop_pos=c(0,0,0,0))
+{
+  pos_set = FALSE
+  t0 = proc.time()
+  # The mother of all nested loops. Makes Ross' and Robert's hearts cringe,
+  # but works. It would be more R-ish to use expand.grid on the `parameters'
[…]

### 2016-11-25 tafaseer_group/retrieval/download.sh

@@ -1,0 +1,81 @@
+#!/bin/bash
+
+session=scraper_session
+madahib=10
+tafaseer=(8 20 10 2 7 7 4 3 5 2)
+last_sura=114
+last_aaya=6
+
+# Opens a new tmux session, preferably ran from outside tmux!
+# I used this for a first run.
+#
+one_process_per_tafsir()
+{
+  tmux new-session -d -s $session || exit
+  i=0; for madhab in `seq 1 $madahib`; do
+    for tafsir in `seq 1 ${tafaseer[$((madhab-1))]}`; do
+      i=$((i+1))
+      tmux new-window -t $session:$i "Rscript download.R --start=$madhab,$tafsir,1,1 --stop=$madhab,$tafsir,$last_sura,$last_aaya"
+    done
+  done
+  tmux attach-session -t $session
+}
+
+# Runs from within tmux, must be in a session first!
+# I used this for running a second time, to grab anything
+# that wasn't downloaded during the first try, because of
+# connection timeouts or whatever. 68 processes was a bit
+# much for running on just 8 cores in hindsight, 10 should
+# be a better fit, especially since the smaller madhahib
+# (with 2 tafaseer each) will finish rather quickly, at
+# which point it will become one process per core.
+#
+one_process_per_madhab()
+{
+  for madhab in `seq 1 $madahib`; do
+    tmux new-window "Rscript download.R --start=$madhab,1,1,1 --stop=$madhab,${tafaseer[$((madhab-1))]},$last_sura,$last_aaya"
+  done
+}
+
+# As per Maxim's wish, downloading by tafsir again,
+# two per core only this time.
+one_tafsir_per_core()
+{
+  histfile=tmp/scraped.dat
+  touch $histfile
+  while true; do
+    cores=1
+    starting_madhab=1
+    starting_tafsir=1
+    instances=$(ps ax | grep 'download.R' | grep -E '([[s]tart|[s]top)' | wc -l)
+    newest_instance=$(ps ax | grep 'download.R' | grep -E '([[s]tart|[s]top)' | tail -1)
+    newest_instance_start_pos=$(echo $newest_instance | cut -d '=' -f 3 | cut -d ' ' -f 1)
+    
+    if [ "$instances" == "" ]; then instances=0; fi
+    if [ "$newest_instance" == "$madahib,$tafaseer[$((madahib-1))],1,1" ]; then
+      echo "All through. Stop."
+      break
+    fi
+
+    for madhab in `seq $starting_madhab $madahib`; do
[…]

### 2016-11-25 tafaseer_group/retrieval/extract.r

@@ -1,0 +1,163 @@
+#!/usr/bin/env Rscript
+# Only runs on R >= 3.3.1
+# Requires: install.packages(c('rvest', 'XML', 'magrittr', 'stringr', 'jsonlite', 'yaml', 'httr', 'optparse', 'stringi'))
+# Remember: every line of code one liability!
+
+for (lib in c('rvest', 'stringr', 'jsonlite', 'yaml', 'httr', 'optparse', 'stringi')) {
+  suppressPackageStartupMessages(library(lib, character.only = TRUE))
+}
+
+# Home-made libraries for the win!
+source(file.path('lib', 'grepx.r'))
+
+paths = list()
+paths$downloaded <- file.path('..', '..', 'corpora', 'altafsir_com', 'downloaded')
+paths$extracted  <- file.path('..', '..', 'corpora', 'altafsir_com', 'extracted')
+paths$quran      <- file.path('..', '..', 'corpora', 'the_quran_by_aaya')
+
+read_dirs <- function(paths, force=FALSE)
+{
+  t0 = proc.time()
+  # Go through sura directories, save sura number
+  for (p1 in Sys.glob(file.path(paths$downloaded, 'quran_???'))) {
+    # Go through aaya directories, save aaya number
+    for (p2 in Sys.glob(file.path(p1, 'aaya_???'))) {
+      # Go through madhab directories, save madhab number
+      for (p3 in Sys.glob(file.path(p2, 'madhab_??'))) {
+        # Go through tafsir directories, save tafsir number
+        for (path in Sys.glob(file.path(p3, 'tafsir_??'))) {
+          message(path)
+          paths$infile <- path
+          data = list() # Whither to put our treasure, arrr!
+          regx = 'quran_(?<sura>\\d{3})/aaya_(?<aaya>\\d{3})/madhab_(?<madhab>\\d{2})/tafsir_(?<tafsir>\\d{2})' 
+          data$position = grepx(regx, path)[[1]] # See lib/grepx.R! # Attn: characters, not integers returned!
+          display_status_message(t0, data$position)
+          # Go through page files
+          paths$outpath = file.path(paths$extracted, 
+            sprintf('quran_%s',  data$position$sura  ),
+            sprintf('aaya_%s',   data$position$aaya  ),
+            sprintf('madhab_%s', data$position$madhab))
+          paths$outfile <- file.path(paths$outpath, sprintf('tafsir_%s.yml', data$position$tafsir))
+          if (file.exists(paths$outfile) && !force) {
[…]

### 2016-11-25 tafaseer_group/retrieval/lib/numeric_to_hindi.rb

@@ -1,0 +1,8 @@
+# Remember: every line of code one liability!
+# Extends Ruby's base class Numeric, so it'll be available both for Integers and for Floats.
+
+class Numeric
+  def to_hindi
+    (self.to_s.chars.map {|c| [c.ord+1584].pack('U')}).join
+  end
+end

### 2016-11-25 tafaseer_group/retrieval/process.rb

@@ -1,0 +1,92 @@
+#!/usr/bin/env ruby
+
+require 'yaml'
+require 'nokogiri'
+require 'fileutils'
+
+path = File.join('..', '..', 'corpora', 'altafsir_com', 'extracted')
+files = Dir.glob(File.join(path, '**', '*.yml'))
+testfile = File.join(path, 'quran_001/aaya_001/madhab_01/tafsir_01.yml')
+
+class TafsirFile
+  def initialize(file)
+    @in_file = file
+  end
+  
+  def self.convert(file)
+    instance = self.new(file)
+    instance.read
+    instance.clean_yaml
+    instance.clean_html
+    instance.write
+  end
+  
+  def read
+    begin
+      @yaml = YAML.load(File.open(@in_file))
+      @html = Nokogiri::HTML.fragment(@yaml['text']) do |config|
+        config.strict.nonet.noent.noblanks
+      end
+      print "#{@in_file} => "
+    rescue
+      puts "Problem parsing '#{@in_file}', aborting."
+      abort
+    end
+  end
+
+  def write
+    @out_file = @in_file.gsub(/extracted/, 'processed')
+    @out_path = @out_file.gsub(/\/tafsir_\d{2}\.yml/, '')
+    begin
+      FileUtils.mkdir_p(@out_path)
+      File.open(@out_file, 'w') {|f| f.write(@yaml.to_yaml)}
+      puts @out_file
+    rescue
+      puts "Problem writing '#{@out_file}', aborting."
+      abort
+    end
+  end
+
+  def clean_yaml
+    %w{sura aaya madhab tafsir}.each {|p| @yaml['position'][p] = @yaml['position'][p].to_i}
+    @yaml['text'] = String.new
+  end
+
+  def clean_html
+    @doc = Nokogiri::HTML.fragment('') do |config|
+      config.strict.nonet.noent.noblanks
+    end
+    builder = Nokogiri::HTML::Builder.with(@doc) do |doc|
+      @html.css('section').each do |section|
+        doc.section {
+          nodes = section.css('div[align="right"][dir="rtl"] font[color]')
+          nodes.each do |node|
+            unless node.inner_text.empty?
+              case node['color']
+                when 'Olive'
+                  css_class = 'poetry_or_grammar'
+                when 'Red'
+                  css_class = 'hadith'
+                when 'ForestGreen'
+                  css_class = 'quran'
+              end
+              if css_class.nil?
+                doc.p {
+                  doc.text node.inner_text
+                }
[…]

### 2016-11-25 tafaseer_group/retrieval/process.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+while true; do ruby process.rb; sleep 10m; done

### 2016-11-25 tafaseer_group/analysis/topicmodel.R
Adding comments and linking to further reading.

@@ -1,5 +1,6 @@
 #!/usr/bin/env Rscript
 
+# TODO: Think about first implementing https://cran.r-project.org/web/packages/ldatuning/vignettes/topics.html
 params = list(
   burnin  = 4000,
   iter    = 2000,
@@ -28,7 +29,13 @@ crunch_lda <- function(dtm, params)
   LDA(
     dtm,
     params$k,
-    method='Gibbs', # Who is he and why do we like him?
+    # Who is he and why do we like him?
+    # Answer Leeroy Jethro is of course our hero. In this case,
+    # because he allows running some LDA steps on multiple processors
+    # and also because he has lower memory requirements than previous
+    # methods. MEMORY USAGE STILL RISES WITH CORPUS SIZE, THOUGH!!!
+    # (Cf. https://cran.r-project.org/web/packages/topicmodels/vignettes/topicmodels.pdf)
+    method='Gibbs', 
     control=params
   )
 }

### 2016-11-27 newspaper_group/code/al-wantan.R
more code and proposal

@@ -5,9 +5,17 @@
 rm(list=ls())## clean the workspace
 setwd("~/Dokumente/islamicate2.0/project/al-watan") # setting working directory
 
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/scrapeR.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/cleanR.R")
 libs<-c("rvest","stringr","tidyr","methods","beepr")
 for(i in 1:length(libs)){
   suppressPackageStartupMessages(library(libs[i], character.only = TRUE))
 }
 
 
+urls<-scan(file="/media/tobias/tobias_wenzel/Newspaper Archive/Al-Watan/alwatan.links", what="character",sep = "\n")
+
+sapply(urls,scrape.article.alwatan)
+scrape.article.alwatan(urls[1])
+
+clean.alwatan("/home/tobias/Dropbox/Dokumente/islamicate2.0/dec2010/")

### 2016-11-27 newspaper_group/code/almasryalyoum.R

@@ -5,8 +5,8 @@ for(i in 1:length(libs)){
 }
 
 source("scrapeR.R")
-source("cleanR.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/cleanR.R")
 
-source.folder<-"/home/tobias/Downloads/almasryalyoum/2010"
+source.folder<-"/home/tobias/Schreibtisch/2010"
 clean.almasryalyoum(source.folder)
 

### 2016-11-27 newspaper_group/code/arabicTM2.r

@@ -44,7 +44,7 @@ enableJIT(3)
 
 
 
- base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced_stem/ahram_stem.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
+ base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced/hespress.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
 
 research_corpus <- as.character(base_corpus$V2)
  output_names <- as.character(base_corpus$V1)
@@ -140,7 +140,7 @@ json <- createJSON(phi = research_corpusAbstracts$phi,
                    R=terms_shown)
 
 #Visulise and start browser
-serVis(json, out.dir = '/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced_stem', open.browser = FALSE)
+serVis(json, out.dir = '/home/tobias/Dropbox/Dokumente/islamicate2.0/vis/hespress', open.browser = FALSE)
 
 ## get the tables
 
@@ -161,7 +161,7 @@ for (i in 1:K){
   phicolnames[i+1] <- paste(head(phi.t.df[order(phi.t.df[,i+1],decreasing=TRUE),], n=7)[,1], sep="", collapse="_")
 }
 colnames(phi.t.df) <- phicolnames
-write.table(phi.t.df, file = '/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced_stem/phi.csv', append = FALSE, quote = FALSE, sep = ",", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE)
+write.table(phi.t.df, file = '/home/tobias/Dropbox/Dokumente/islamicate2.0/vis/hespress/phi.csv', append = FALSE, quote = FALSE, sep = ",", eol = "\n", na = "NA", dec = ".", row.names = FALSE, col.names = TRUE)
 
 ## get document-topic distributions and export as csv
 theta.frame <- data.frame(matrix(nrow=length(theta[,1]), ncol = K+1))
@@ -172,7 +172,7 @@ for (i in 1:K){
 thetacolnames <- phicolnames
 thetacolnames[1] <- "identifier"
 colnames(theta.frame) <- thetacolnames
[…]

### 2016-11-27 newspaper_group/code/basic_functions.R

@@ -23,4 +23,31 @@ getLinks <- function(homepage.url,link.element){
   homepages.v<-homepages.v[homepages.v!=""]
   return(homepages.v)
 }
+# padding.
+SPRINTF <- function(x) sprintf("%02d", x)
 
+
+f.replaceMonthNames<- function(corpus,month.col=2){
+  Sys.setlocale("LC_TIME", "ar_AE.utf8");
+  month.dates<-seq(as.Date("2012-01-01"), as.Date("2012-12-31"), "months")
+  month.names<-format(month.dates, "%B")
+  
+  for(i in 1:11){
+    corpus[which(corpus[,month.col]==month.names[i]),month.col]<-i
+  }
+  
+  corpus[which(corpus[,month.col]== "دجنبر"),month.col]<-12
+  corpus[which(corpus[,month.col]== "ديسمبر"),month.col]<-12
+  corpus[which(corpus[,month.col]== "نونبر"),month.col]<-11
+  corpus[which(corpus[,month.col]== "اكتوبر"),month.col]<-10
+  
+  
+  corpus[which(corpus[,month.col]== "شتنبر"),month.col]<-9
+  corpus[which(corpus[,month.col]== "غشت"),month.col]<-8
+  corpus[which(corpus[,month.col]== "غشت"),month.col]<-8
+  corpus[which(corpus[,month.col]== "يوليوز"),month.col]<-5
+  corpus[which(corpus[,month.col]== "ابريل"),month.col]<-4
+  
+  
+  return(corpus)
+}

### 2016-11-27 newspaper_group/code/cleanR.R

@@ -19,8 +19,8 @@ clean.almasryalyoum <- function(source.folder){
       
       title.c<- article.homepage %>% html_nodes(xpath="//font[@color='#AB0202'and @size='5']//b") %>% html_text()
       # date extraction see ahram
-      
-      text.c<-paste(article.homepage %>% html_nodes(xpath="//font[@size='2' and @face='Tahoma']//p") %>% html_text(),collapse = " ")
+      text.c <- article.homepage %>% html_nodes(xpath="//font[@size='2' and @face='Tahoma']//p") %>% html_text()
+      text.c<-paste(text.c,collapse = " ")
       
       
       ### dann haben wir halt erstmal kein datum.
@@ -36,10 +36,15 @@ clean.almasryalyoum <- function(source.folder){
       # year<-date[[1]][4]
       ## there seems to be "garbage" at the end of some texts. we should exclude non-arabic letter, i.e. a-Z
       
+      text.c <-sub("\"","",text.c)
+      title.c <- gsub("\"","",title.c)
       
       ## since all homepages look the same I can skip the if-statements (cf. al-watan.R)
-      write.table(data.frame(i,sub("\"","",text.c),gsub("\"","",title.c)),col.names = FALSE,row.names = FALSE,paste(source.folder,".csv",sep=""),sep = ",",quote = "",fileEncoding = "UTF-8",append = T)
-      i<-i+1
+      if(nchar(text.c)>10){
+      write.table(data.frame(i,text.c),col.names = FALSE,row.names = FALSE,paste(source.folder,".csv",sep=""),sep = "\t",fileEncoding = "UTF-8",append = T)
+      #write.table(data.frame(i,sub("\"","",text.c),gsub("\"","",title.c)),col.names = FALSE,row.names = FALSE,paste(source.folder,".csv",sep=""),sep = "\t",fileEncoding = "UTF-8",append = T)
+         i<-i+1
+      }
     },error =function(e){write(paste("page",my.filename,"could not be loaded",sep=" "),"log",append = TRUE )})
     
   }
@@ -108,6 +113,7 @@ clean.alwatan<- function(source.dir){
         text.c<-homepage %>%
           html_nodes("span#ctl00_ContentPlaceHolder1_lblDescription") %>% html_text()
         year<-str_sub(my.filename,-8,-5)
+        
         month<-str_sub(my.filename,-4,-3)
         day<-str_sub(my.filename,-2,-1)
       }
[…]

### 2016-11-27 newspaper_group/code/hespress.R

@@ -18,7 +18,7 @@ source("scrapeR.R")
 source("cleanR.R")
 
 
-
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/cleanR.R")
 ###############################################################################
 ##                          CALLING THE SCRIPTS
 ###############################################################################
@@ -47,5 +47,5 @@ option_list = list(
 ); o = parse_args(OptionParser(option_list=option_list))
 
 #scrape.day(o$day)
-#source.folder<- "hespress2011"
-#clean.hespress(source.folder)
+source.folder<- "/home/tobias/Schreibtisch/hespress2010"
+clean.hespress(source.folder)

### 2016-11-27 newspaper_group/code/scrapeR.R

@@ -137,6 +137,30 @@ scrape.day.ahram<- function(day.to.observe){
   }# end of for-loop
 } # end of scrapeRaw-function
 
+scrape.article.alwatan <- function(homepage.url.article){
+  ## would be even better to pass filenames as vectors.
+  target.folder<-"/home/tobias/Dropbox/Dokumente/islamicate2.0/dec2010"
+  my.filename <- paste(target.folder,"/", gsub("/", "_", homepage.url.article),".html", sep = "")
+
+  if(!file.exists(my.filename)){
+   
+    tryCatch({
+      homepage.day.article<-read_html(homepage.url.article,encoding = "UTF-8")
+      write_xml(homepage.day.article,my.filename)
+      
+      sleep(0.1)}
+      ,error = function(e){
+        print(paste("error while loading",homepage.url.article,sep=" "))
+     
+      })
+    
+  }# end of file.exists
+  else{
+    print(paste("skip",homepage.url.article,"because i have it already.",sep=" "))
+  }
+}
+
+
 # e.g. facebook,twitter-links.
 filter_homepages.ahram<-function(homepages.v){
   # i should scrape everything first...

### 2016-11-27 newspaper_group/code/tests.R

@@ -4,132 +4,124 @@ rm(list=ls())
 
 # might be nec. to change this.
 
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/basic_functions.R")
 
 # 
-# ####
-# corpus2011<-read.csv(file="/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/data/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F )
-# corpus2010<-read.csv(file="/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/data/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+# # ####
+#  corpus2011<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F )
+#  corpus2010<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+#  corpus2010<-corpus2010[corpus2010$V4!="",]
+#  corpus2011<-corpus2011[corpus2011$V4!="",]
+#  # 
+# # 
+#  corpus2011<-f.replaceMonthNames(corpus2011,month.col = 2)
+#  corpus2010<-f.replaceMonthNames(corpus2010,month.col = 2)
+# # 
+# # 
+# # 
 # 
+#  dec<-corpus2010[which(corpus2010$V2==12),]
 # 
-# corpus2011<-f.replaceMonthNames(corpus2011,month.col = 2)
-# corpus2010<-f.replaceMonthNames(corpus2010,month.col = 2)
-# 
-# 
-# 
-f.replaceMonthNames<- function(corpus,month.col=2){
-  Sys.setlocale("LC_TIME", "ar_AE.utf8");
-  month.dates<-seq(as.Date("2012-01-01"), as.Date("2012-12-31"), "months")
-  month.names<-format(month.dates, "%B")
-
-  for(i in 1:11){
-    corpus[which(corpus[,month.col]==month.names[i]),month.col]<-i
-  }
-
[…]

### 2016-11-27 newspaper_group/code/thawra.R

@@ -11,6 +11,7 @@ for(i in 1:length(libs)){
   suppressPackageStartupMessages(library(libs[i], character.only = TRUE))
 }
 source("basic_functions.R")
+source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/cleanR.R")
 
 # actually not needed.
 #setwd("~/Dokumente/islamicate2.0/project/hespress") # setting working directory
@@ -21,4 +22,5 @@ base.url<-"http://thawra.sy/"
 tharwa.urls <- scan("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/thawra_urls_2014.txt", what="", sep="\n")
 lapply(tharwa.urls,scrape.day.thawra)
 
-
+source.folder<- "/home/tobias/Schreibtisch/tharwa"
+clean.thawra(source.folder)

### 2016-12-02 newspaper_group/code/arabicTM2.r
code doc

@@ -44,7 +44,7 @@ enableJIT(3)
 
 
 
- base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced/hespress.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
+ base_corpus <- read.table("/home/tobias/Dropbox/Dokumente/islamicate2.0/reduced/hespress_c.csv", sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
 
 research_corpus <- as.character(base_corpus$V2)
  output_names <- as.character(base_corpus$V1)
@@ -55,6 +55,17 @@ research_corpus <- gsub("[[:cntrl:]]", " ", research_corpus)  # replace control 
 research_corpus <- gsub("^[[:space:]]+", "", research_corpus) # remove whitespace at beginning of documents
 research_corpus <- gsub("[[:space:]]+$", "", research_corpus) # remove whitespace at end of documents
 research_corpus <- gsub("[0-9]", "", research_corpus) #remove numbers
+
+#research_corpus<-sapply(research_corpus, gsub, "[[:ascii]]","", perl=T)
+
+
+# research_corpus<-sapply(research_corpus,gsub,"[[:punct:]]", " ")  # replace punctuation with space
+# research_corpus<-sapply(research_corpus,"[[:cntrl:]]", " ", research_corpus)  # replace control characters with space
+# research_corpus<-sapply(research_corpus,"^[[:space:]]+", "", research_corpus) # remove whitespace at beginning of documents
+# research_corpus<-sapply(research_corpus,"[[:space:]]+$", "", research_corpus) # remove whitespace at end of documents
+# research_corpus<-sapply(research_corpus, gsub, "[0-9]"," ")
+
+
 
 
 # tokenize on space and output as a list:
@@ -84,7 +95,7 @@ term.table <- sort(term.table, decreasing = TRUE)
 
 
 # remove terms that are stop words or occur fewer than "occurenses" times:
-occurences <- 5
+occurences <- 10
 
 del <- names(term.table) %in% stop_words | term.table < occurences 
 term.table <- term.table[!del]

### 2016-12-02 newspaper_group/code/scrapeR.R

@@ -8,182 +8,218 @@
 ###############################################################################
 ##                              HESPRESS
 ###############################################################################
-
-scrape.index.hespress<- function(day.links,target.folder){
+scrape.index.hespress <- function(day.links, target.folder) {
+  # Scrape all articles which are linked on the current index-page
+  # of the day.
+  #
+  # Called by: scrape.day.hespress
+  # Args:
+  #   day.links: A list of links to index pages.
+  #   target.folder: A character string to set the target folder.
   for (link in day.links) {
     file <- paste(target.folder, gsub("/", "_", link), sep = "")
     ## if the file is already downloaded, skip it.
     if (!file.exists(file)) {
       tryCatch({
-        article.homepage<-read_html(curl(paste("http://www.hespress.com", link, sep = ""), handle = curl::new_handle("useragent" = "Mozilla/5.0")), encoding = "UTF-8")
+        article.homepage <- read_html(curl(
+            paste("http://www.hespress.com", link, sep = ""),
+            handle = curl::new_handle("useragent" = "Mozilla/5.0")
+          ), encoding = "UTF-8")
         write_xml(article.homepage, file)
         sleep(0.1)
-      }
-      , error = function(e) {
-        write(gsub("/", "_", link),
-              paste(target.folder,"missed.log",sep=""),
+      } , error = function(e) {
+        write(link,
+              paste(target.folder, "missed.log", sep = ""),
               append = TRUE)
-      })
-    }
-  }
-  
-}
+      })  # end of tryCatch
+    }  # end of if file.exists
+  }  # end of for-loop
+}  # end of scrape.index.hespress
 
-
-scrape.day.hespress <- function(hespress.url) {
-  target.folder<-"~/Downloads/hespress2016/" ##"~/Dokumente/islamicate2.0/hw/corpora/newspaper_archive/Hespress/hespress2015/"
+scrape.day.hespress <- function(hespress.url, target.folder) {
+  # Navigate to all top level index pages which have links to articles.
+  # The algorithm stops when all of the index pages have been checked.
+  # The actual scraping is done in scrape.index.hespress
+  #
+  # Args:
+  #   hespress.url: Link to the first index-page of the day.
+  #   target.folder: A character string to set the target folder.
   
[…]

### 2016-12-02 newspaper_group/code/tests.R

@@ -8,39 +8,39 @@ source("/home/tobias/Dokumente/islamicate2.0/hw/newspaper_group/code/basic_funct
 
 # 
 # # ####
-#  corpus2011<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F )
-#  corpus2010<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
-#  corpus2010<-corpus2010[corpus2010$V4!="",]
-#  corpus2011<-corpus2011[corpus2011$V4!="",]
+ corpus2011<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2011.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F )
+ corpus2010<-read.csv(file="/home/tobias/Schreibtisch/Newspaper Corpus/Hespress/hespress2010.csv",fileEncoding = "UTF-8",sep=",",header = FALSE,stringsAsFactors=F)
+ corpus2010<-corpus2010[corpus2010$V4!="",]
+ corpus2011<-corpus2011[corpus2011$V4!="",]
 #  # 
 # # 
-#  corpus2011<-f.replaceMonthNames(corpus2011,month.col = 2)
-#  corpus2010<-f.replaceMonthNames(corpus2010,month.col = 2)
+  corpus2011<-f.replaceMonthNames(corpus2011,month.col = 2)
+  corpus2010<-f.replaceMonthNames(corpus2010,month.col = 2)
 # # 
 # # 
 # # 
 # 
-#  dec<-corpus2010[which(corpus2010$V2==12),]
+  dec<-corpus2010[which(corpus2010$V2==12),]
 # 
 # 
-# ids<-1:dim(dec)[1]
-#  uri<-paste("HP",dec$V1,dec$V2,SPRINTF(dec$V3),"$",ids,sep = "")
-# 
-#  new.corpus<-data.frame(uri,dec$V4 ,stringsAsFactors = F)
[…]

### 2016-12-02 newspaper_group/code/text_analysisJM.R

@@ -11,6 +11,7 @@ library(arabicStemR)
 
 library(wordcloud)   
 
+#library(bigmemory)
 ### set the directory with files. you might have several corpuses or one file for each article
 #### just skipt this for at this moment.
 
@@ -24,53 +25,116 @@ library(wordcloud)
 
 ### an alternative way to load data
 ## you have to set header=FALSE
-filename<-"/home/tobias/Dropbox/Dokumente/islamicate2.0/reducedfiles/alwatan_stem_tr.csv"
-base_corpus <- read.table(filename, sep=",", header=FALSE,encoding = "UTF-8",stringsAsFactors = F)
 
-data <- read.csv(filename, encoding = "UTF-8",sep = ",",header = FALSE,stringsAsFactors=F)
+as.big.matrix <- function(x) {
+  nr <- x$nrow
+  nc <- x$ncol
+  # nr and nc are integers. 1 is double. Double * integer -> double
+  y <- matrix(vector(typeof(x$v), 1 * nr * nc), nr, nc)
+  y[cbind(x$i, x$j)] <- x$v
+  dimnames(y) <- x$dimnames
+  y
+}
+ 
+getMfw <- function(data, n){
+  
+  
+  
+  data[,2] <- gsub("[[:punct:]]", " ", data[,2])  # replace punctuation with space
+  data[,2] <- gsub("[[:cntrl:]]", " ", data[,2])  # replace control characters with space
+  data[,2] <- gsub("[0-9]", " ", data[,2]) #remove numbers
+  data[,2] <- gsub("^[[:space:]]+", "", data[,2]) # remove whitespace at beginning of documents
+  data[,2] <- gsub("[[:space:]]+$", "", data[,2]) # remove whitespace at end of documents
 
-### some additional cleaning.
+#  data<-data[1:5000,]## more is resulting in memory overflow
 
-data[,2] <- gsub("[[:punct:]]", " ", data[,2])  # replace punctuation with space
-# data[,2] <- gsub("[[:cntrl:]]", " ", data[,2])  # replace control characters with space
-# data[,2] <- gsub("^[[:space:]]+", "", data[,2]) # remove whitespace at beginning of documents
-# data[,2] <- gsub("[[:space:]]+$", "", data[,2]) # remove whitespace at end of documents
[…]

### 2016-12-15 tafaseer_group/03_results/Paper.Rmd
The beginnings of Thom's work.

---
title: Badʾ al-masīr fī taʾrīḫ al-tafsīr--An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
 Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
subtitle: Universities of Leipzig and Maryland
author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it using by identifying number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran). Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
output: pdf_document
toc: no
fontsize: 12pt
geometry: margin=1.5in
lang: en
documentclass: article
latex_engine: xelatex
urlcolor: blue
---

# 1 Introduction

How has Islamic interpretation of the Quran changed over time? Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time? Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another? Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration? To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format. As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*. The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*. This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on. The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts that are derived from various traditions, sects, and schools of jurisprudence. That desired breadth has yet to be achieved. The website currently has seventeen complete tafasīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.

Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every verse-specific chunk of the commentary and dividing that number by the total word count of the *tafsīr*. It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*. Importance might not necessarily mean that the *mufassir* had an increased affinity for the values or instructions espoused in the verse. A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the Muslim layman and therefore devoted more writing to explication and contextualizing.

When we sorted the verses from most written about to least, we observed some suspicious patterns. Consecutive verses were appearing next to one another on the list and they had identical word counts. When we inspected the files in our corpus, we found that there were duplicate chunks of text. The problem was that most of the writers alternated between writing about singles verses and writing about groups of consecutive verses that dealt with a single narrative or theme. If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website. When the script to download the tafasīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse. Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem.

We ran a script that looked for duplicate texts and removed any repeated segments. Since we were not able to get word counts for specific verses, we decided to focus on the *sūra* or chapters of the Quran. There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest. We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting. We looked at the top twenty-five *sūrāt* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two. The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.

## 1.1 The Groupings

![Gephi social network analysis result](../02_analysis/data_manual/gephi/mufasirooncomparison.png)

The data as described so far was run through the Gephi social network analysis program. The algorithm calculated four distinct groups, represented as colors in figure 1. They are as follows:

1. *Ibnu-l-Ǧauzī*, *at-Tabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
2. *az-Zamaḫšarī*, *al-Baiḍāwī*, and *an-Nasafī*
3. *ar-Rāzī*, *al-Fayrūzabādī*, *al-Qurṭubī*, *al-Khāzin*, and *Abū Ḥayyān*
4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdu-s-Salām*

# 1 The corpus
## 1.1 Data origin and possible intentions behind its compilation
## 1.2 Data extraction and transformation into processable outer form
## 1.3 Authors of the 18 works
### 1.3.1 d. 728: Jarir ibn Atiyah (Yamamah, Damascus)
### 1.3.2 d. 925: Muhammad ibn Zakariya al-Razi (Rey)
### 1.3.3 d. 923: Al-Tabari (Amol-Baghdad)
### 1.3.4 d. 971: Abū Ja'far al-Khāzin (Iran?)
### 1.3.5 d. 1044: Al-Baghawi (?)
### 1.3.6 d. 1058: Al-Mawardi (Basrah-Baghdad)
### 1.3.7 d. 1142: Abu Hafs Umar an-Nasafi (Nakhshab-Samarqand)
### 1.3.8 d. 1144: Al-Zamakhshari (Kwharezm-Mecca-Khwarezm)
### 1.3.9 d. 1201: Ibn al-Jawzi (Baghdad)
### 1.3.10 d. 1261: Ibn 'Abd as-Salam (Damascus-Egypt)
### 1.3.11 d. 1273: Al-Qurtubi (Cortoba)
### 1.3.12 d. 1286: Al-Baydawi (Shiraz-Tabriz)
### 1.3.13 d. 1310: Shams al-Dīn al-Samarqandī (Samarqand)
### 1.3.14 d. 1401: Ibn Arafa (Tunis)
### 1.3.15 d. 1414: Fairuzabadi (Fars-Mekka)
### 1.3.16 d. 1505: Al-Suyuti (Cairo)
### 1.3.17 d. 1344: Abu Hayyan al-Gharnati (Spain-Cairo)
### 1.3.18 d. 1373: Ibn Kathir (Bosra-Damascus)
# 1.4 Conventional categorisation and inter-relationships of the authors
# 2 Analysis
# 2.1 Most frequent words (MFW), Zipf's law
# 2.2 Stylometrics
# 2.3 Topic Modelling results
# 2.4 Congruences of observations with conventional views
# 2.5 Notable differences to conventional views
# 3 Conclusion
# 3.1 Possible theses based on findings
# 3.2 Discussion of necessary further work
# 4 Bibliography

### 2016-12-15 tafaseer_group/03_results/Paper.Rmd
Changes suggested by Thom.

@@
 Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem.
+Of the 87 *tafsīr* works listed on the website, 69 turned out to be completely empty and one author, *Ibn ʿArafa*, only provided commentary on *sūratān*.
+Both were removed from the corpus used for analysis, which consequently consists of 17 works comprising $i_{total}=16444304$ words.
 
@@
 4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdu-s-Salām*
+
+TODO: disambiguate mufassir names wherever they end up appearing first.
+Here's the unclear ones (mails from Dec 15): There is more than one al-Razi and Ibn atiyah.
+Our al-Razi is Fakhr al-Din and our ibn atiya is ibn atiya al-andalusi.
+And al- khazin is Ala' al-din al-khazin.
 

### 2016-12-16 tafaseer_group/03_results/Paper.Rmd

@@
 ---
-title: Badʾ al-masīr fī taʾrīḫ al-tafsīr--An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
+title: Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th
  Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
@@
 tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
-abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it using by identifying number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran).
+abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran).
 Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
@@
 To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format.
+
+# 2 The corpus
+
 As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
@@
 That desired breadth has yet to be achieved.
-The website currently has seventeen complete tafasīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.
+The website currently has seventeen complete tafāsīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.
+
+# 3 Exploratory data analysis
 
@@
 If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website.
-When the script to download the tafasīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse.
+When the script to download the tafāsīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse.
 Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem.
@@
 We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting.
-We looked at the top twenty-five *sūrāt* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
+We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
 The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.
 
-## 1.1 The Groupings
+## 3.1 The Groupings
 
@@
 
-1. *Ibnu-l-Ǧauzī*, *at-Tabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
-2. *az-Zamaḫšarī*, *al-Baiḍāwī*, and *an-Nasafī*
-3. *ar-Rāzī*, *al-Fayrūzabādī*, *al-Qurṭubī*, *al-Khāzin*, and *Abū Ḥayyān*
-4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdu-s-Salām*
+1. *Ibnu-l-Ǧawzī*, *aṭ-Ṭabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
+2. *az-Zamaḫšarī*, *al-Bayḍāwī*, and *an-Nasafī*
+3. *ar-Rāzī*, *al-Fayrūzābādī*, *al-Qurṭubī*, *al-Ḫāzin*, and *Abū Ḥayyān*
+4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdi-s-Salām*
+
+# 4 Bibliography
+
+Blah blah blah
+
+# Appendix
 
 TODO: disambiguate mufassir names wherever they end up appearing first.
-Here's the unclear ones (mails from Dec 15): There is more than one al-Razi and Ibn atiyah.
+Here's the unclear ones (mails from Dec 15): "There is more than one al-Razi and Ibn atiyah.
 Our al-Razi is Fakhr al-Din and our ibn atiya is ibn atiya al-andalusi.
-And al- khazin is Ala' al-din al-khazin.
+And al- khazin is Ala' al-din al-khazin."
 
-# 1 The corpus
+TODO: remove below draft headings before handing the paper in!
+
 ## 1.1 Data origin and possible intentions behind its compilation
@@
 # 3.2 Discussion of necessary further work
-# 4 Bibliography

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
Adding new additions from the Google document.

@@
 
+# 2 The Tafasir
+
+TODO: DMGize
+
+al-Bahr al-Muhit by Abu Hayyan
+al-Jami' li Ahkam al-Qur'an by al-Qurtubi
+al-Kashshaaf by al-Zamakhshari 
+al-Muharrar al-Wajiz fi Tafsir al-Kitaab al-'Aziz by Ibn Atiyyah
+Al-Nukat wal 'Uyuun by al-Mawardi
+Anwar al-Tanzil wa Asrar al-Ta’wil by al-Baydawi
+Bahr al-Uluum by al-Samarqandi
+Jami` al-bayan `an Ta'wil 'ay al-Qur'an by al-Tabari
+Lubab al-Ta'wil fi Ma'ani al-Tanzil by al-Khazin
+Ma’alm al-Tanzil by al-Baghawi
+Madarik al-Tanzil wa Haqa'iq al-Ta'wil by al-Nasafi
+Mafatih al-Ghayb by al-Razi
+Tafsir al-Jalalayn by al-Mahali and al-Suyuti
+Tafsir al-Qur'an by al-Fairuzabadi
+Tafsir al-Qur’an by Ibn Abd-al-Salam
+Tafsir al-Qur'an al-Azim by Ibn Kathir
+Zad al-Masir fi 'ilm al-Tafsir by Ibn al-Jawzi
+
 # 2 The corpus
@@
 This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on.
-The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts that are derived from various traditions, sects, and schools of jurisprudence.
+The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts originating from various traditions, sects, and schools of jurisprudence.
 That desired breadth has yet to be achieved.
@@
 
-# 3 Exploratory data analysis
+# 3 Methodology
 
-Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every verse-specific chunk of the commentary and dividing that number by the total word count of the *tafsīr*.
+Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the tafsir that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*.
 It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*.
@@
 
-## 3.1 The Groupings
+## 3.1 The Results
 
@@
 
-1. *Ibnu-l-Ǧawzī*, *aṭ-Ṭabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
-2. *az-Zamaḫšarī*, *al-Bayḍāwī*, and *an-Nasafī*
-3. *ar-Rāzī*, *al-Fayrūzābādī*, *al-Qurṭubī*, *al-Ḫāzin*, and *Abū Ḥayyān*
-4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdi-s-Salām*
+1. Green: *Ibnu-l-Ǧawzī* (d. 597 AH),, *aṭ-Ṭabarī* (d. 310 AH), *Ibn Kaṯīr* (d. 774 AH), *Ibn ʿAṭīya* (d. 546 AH), and *al-Baġawī* (d. 516 AH)
+2. Blue: *az-Zamaḫšarī* (d. 538 AH), *al-Bayḍāwī* (d. 685 AH), and *an-Nasafī* (d. 710 AH)
+3. Purple: *ar-Rāzī* (d. 606 AH), *al-Fayrūzābādī* (d. 817 AH), *al-Qurṭubī* (d. 671 AH), *al-Ḫāzin* (d. 741 AH), and *Abū Ḥayyān* (d. 754 AH)
+4. Orange: *al-Maḥallī* (d. 864 AH) and *as-Suyūṭī* (d. 911 AH), *as-Samarqandī* (d. 375 AH), *al-Māwardī* (d. 450 AH), and *Ibn ʿAbdi-s-Salām* (d. 660 AH)
 
-# 4 Bibliography
+TODO: DMGize, mark citations
 
-Blah blah blah
+The unifying characteristic for the exegetes of the first cluster is their reputation as traditionalists.
+Al-Tabari saw his method of tafsir bil-mathur, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of bid’ah or heretical innovation (Bauer, 2013).
+Al-Baghawi emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muhammad or the sahaba, the companions of Muhammad (Robson, n.d.).
+Hanbali adherent Ibn al-Jawzi campaigned against the Shia in Iraq and authored a paean celebrating the end of Ismaili Fatimid rule in Egypt and the accession of a Sunni, Salah al-Din, to power (Mallett, n.d.).
+Ibn Atiyyah’s exegesis received praise from Ibn Taymiyyah, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (Salahi, 2002).
+The inclusion of Ibn Taymiyyah’s student Ibn Kathir can be attributed to either his conservative leanings—he penned a defense of armed Jihad against neighboring non-Muslim states (Laoust, n.d.)—or to his tafsir being, as some scholars have observed, a summarized version of al-Tabari’s (McAuliffe, 1991).
+
+TODO: DMGize, mark citations
+
+For the second cluster, geography seems to be the unifying factor.
+Arabic grammarian and Mu’tazila partisan al-Zamakhshari (McAuliffe, 1991) differed from Hanafi jurist al-Nasafi on matters of doctrine (Poonawala, Wensinck & Heffening, n.d.) but they both lived in the Central Asian region known as Ma wara al-Nahr (Transoxiana) while the Shafi’i al-Baydawi lived in what is now Iran (Krauss-Sánchez, n.d.).
+Al-Baydawi’s exegesis Anwar al-tanzil wa asrar al-ta'wil has been labeled an amended version of al-Zamakhshari’s al-Kashshaaf, with Mu’tazila philosophy and other perceived heresies expunged from the text (McAuliffe, 1991).
+This grouping may reflect a unique Central Asian outlook to the Quran and the addition of al-Baydawi may result from his reliance on the work of al-Zamakhshari.
+
+TODO: DMGize, mark citations
+
+If there is a latent, unifying factor to the mufasiroon of the third cluster, it is not immediately apparent to us.
+The exegetes were not contemporaneous to one another with al-Razi preceding al-Fairuzabadi by two centuries.
+Geography certainly did not connect the writers.
+Abu Hayyan (Glazer & Homerin, n.d.) and al-Qurtubi were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
+Al-Khazin lived in Syria which also was briefly the home of Persian-born al-Fairuzabadi who also spent his life in Jerusalem, Mecca, and Yemen (Fleisch, n.d.).
+Al-Razi lived in what is now Iran and Afghanistan (McAuliffe, 1991).
+In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of Mu’tazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta’wil or figurative reading in Quranic interpretation (Jaffer, 2015).
+Unfortunately, the inability to obtain word counts at the verse-level and therefore our inspection at the chapter-level may have adversely affected the quality of the groupings calculated by Gephi.
+
+TODO: DMGize, mark citations
+
+The last cluster of our analysis resulted in a predictable grouping of exegetes.
+The primary characteristic that unified these authors was their choice of school of jurisprudence.
+Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
+Amongst the four authors in this cluster three were from the school of Shafi’i and one from the school of Hanafi.
+
+TODO: DMGize, mark citations
+
+Al–Mawardi was an Islamic jurist born in Basra, Iraq during 364AH (Sharif, 2002).
+During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
+The cities where al-mawari lived where known to be hubs of the Mu’tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu’tazaila jurisprudence) was in fact associated with the Shafi’i school of thought.
+He was later condemned for his Mu'tazila sympathies.
+Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of Shafi’i.
+Amongst the four jurist the Caliph favored Al-Mawardi and appointed chief imam.
+(Sharif, 2002) Along with the school of jurisprudence a common factor amongst most of the authors was their interest or relation in Islamic law.
+
+TODO: DMGize, mark citations
+
+Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and Al–Mawardi.
+During his time he was the leading authority in the Shafi’i Jurisprudence and most famous for his interpretations of Islamic legal principles.
+Unlike al mawari ,Abd al-Salam was known to be defiant of customs he deemed “unsanctioned”.
+He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus As-Salih Ismail.(Jackson, 1996)  This condemning led to his imprisonment and eventual emigration to Cairo, Egypt.
+In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt.
+(Salahi) Like Al-Mawardi, Al- Salam was a world renowned scholar of fatwas.
+Al-salam was so respected, islamic jurist like al-Hafiz al-Mundhiri stopped giving fatwas stating "It does not behove any jurist to give a fatwa where Izz al-Din(Ibn 'Abd al-Salam) happens to be present."(Salahi) Both Ibn 'Abd al-Salam and Al-Mawardi were highly respected scholars of their time especially in regards to islamic law.
+Both authors were advisors to their respected islamic governments of their time,(Jackson, 1996)  another factor which may have attributed to the groups of these authors in the same cluster.
+
+TODO: DMGize, mark citations
+
+Jalal al-Din al-Suyuti was born in Cario, Eygpt in the year 849AH (al-Suyuti, 2007) making his work the most recent amongst the cluster.
+Like most authors in the cluster he was a islamic jurist from the school of shafi’i.
+He was acknowledged as one of the more recent authority of the Shafi’i school whose degree of ijthad was accepted by most(Meri,2005).
+Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
+Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the Hanafi school of jurisprudence and was tutored by a Sufi, though his work drew primarily from shafi’i school of thought.
+Al-Suyuti’s interest in the Hanafi jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
+
+TODO: DMGize, mark citations
+
+Abu al-Layth al-Samarqandi author of Bahr Ul ‘Ulum was the single author in the cluster from the school of Hanafi.
+Apart from his jurisprudence another outlying factor for al-Samaraqandi was his geographical location and time period.
+He was born in Afghanistan during 373AH making him the oldest exegete in this cluster.
+(wheeler, 2002) Since his worked dated back so far we were unable to find much information in regards to his lifestyle or any other factors that may have attributed to his placing in this cluster although, however we were able to compile a few specific features of his exegesis.
+In his work of the Quran al-samarqandi was known to relate the stories of sahabah and other hadiths from people not proven to be 100% reliable.
+He was also known for his lack of interest in the various methods of recitation (Qira’at).(“Liste..” 2002)  Unfortunately, due to lack of information on Al Samarqandi we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
+
+TODO: DMGize, mark citations
+
+From the results of the study, we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of the paper (chronology, geography, dogma).
+However, we believe that examination of surah and ayah preference from Quranic exegetes deserves further exploration.
+
+# 4 References
+
+TODO: Move into Biblatex file, reference properly in the text, have it built automatically.
+
+"Al-Suyuti." Encyclopedia Britannica Online. May 16, 2007. Accessed December 1, 2016. https://www.britannica.com/biography/al-Suyuti.
+
+Bastian M., Heymann S., Jacomy M. (2009). Gephi: an open source software for exploring and manipulating networks. International AAAI Conference on Weblogs and Social Media
+
+Bauer, Karen (2013).
+“A Study of Introductions to Classical Works of Tafsir”,  in Karen Bauer (Ed) Aims, Methods and Contexts of Qur’anic Exegesis: (2nd/8th-9th/15th C.) (39-65).
+New York, NY: Oxford University Press.
+
+Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
+
+Fleisch, H., “al-Fīrūzābādī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
+
+Glazer, Sidney and Homerin, Th.
+Emil, “Abū Ḥayyān al-Gharnāṭī”, in: Encyclopaedia of Islam, THREE, Edited by: Kate Fleet, Gudrun Krämer, Denis Matringe, John Nawas, Everett Rowson.
+Retrieved from http://www.brillonline.com
+
+Jackson, Sherman A(1996). Islamic law and the state: the constitutional jurisprudence of Shihāb al-Dīn al-Qarāfī. Leiden: E.J. Brill, 1996.
+
+Jaffer, Tariq (2015). Razi: Master of Qur’anic Interpretation and Theological Reasoning. New York, NY: Oxford University Press.
+
+Krauss-Sánchez, Heidi R., “al-Baydāwī”, in: Encyclopedia of the Medieval Chronicle, Edited by: Graeme Dunphy, Cristian Bratu. First Published online 2016.  Retrieved
+From http://www.brillonline.com
+
+Laoust, H., “Ibn Kat̲h̲īr”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
+
+"Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.
+
+Mallett, Alex, “Ibn al-Jawzī”, in: Christian-Muslim Relations 600 - 1500, General Editor David Thomas. Retrieved From http://www.brillonline.com
+
+Meri, Josef W., ed. (2005). "Suyuti, Al-, 'Abd al-Rahman". Medieval Islamic Civilization: An Encyclopedia. Routledge. pp. 784–786.
+
+McAuliffe, Jane Dammen (1991). Qur’anic Christians: An Analysis of Classical and Modern Exegesis. New York, NY: Cambridge University Press.
+
+Poonawala, I., Wensinck, A.J.
+and Heffening, W., “al-Nasafī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P.
+Bearman, Th.
+Bianquis, C.E.
+Bosworth, E.
+van Donzel, W.P.
+Heinrichs.
+Retrieved from http://www.brillonline.com
+
+Robson, J., “al-Bag̲h̲awī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://brillonline.com
+
+Salahi, Adil (2002, October 14). Scholar of Renown: Ibn Atiyyah. Arab News. Retrieved from http://www.arabnews.com
+
+Salahi , Adil. "Izz Al-Din ibn Abd Al-Salam." Izz Al-Din ibn Abd Al-Salam | Muslim Heritage. Accessed December 1, 2016. http://www.muslimheritage.com/article/izz-al-din-ibn-abd-al-salam.
+
+Sharif , M M. "Al-MĀWARDĪ." Encyclopaedia of Islam, Second Edition1, no. 3 (August 8, 2002). Accessed December 1, 2016. doi:10.1163/1573-3912_islam_com_0713.
+
+Wheeler, Brannon M. Prophets in the Quran: an introduction to the Quran and Muslim exegesis. London: Continuum, 2002.
+pg 337
+
+Zahoor, A., Dr. "Al-Mawardi, 972-1058 C.E." Al-Mawardi, 972-1058 C.E. January 15, 1998. Accessed December 1, 2016. http://www.unhas.ac.id/rhiza/arsip/saintis/mawardi.html.
 
@@
 
-TODO: disambiguate mufassir names wherever they end up appearing first.
-Here's the unclear ones (mails from Dec 15): "There is more than one al-Razi and Ibn atiyah.
-Our al-Razi is Fakhr al-Din and our ibn atiya is ibn atiya al-andalusi.
-And al- khazin is Ala' al-din al-khazin."
+Note: as this document was prepared using the `rmarkdown` package, consequently `knitr`'s built-in devices are being used to include our source code in the below appendices for reference.
+Unfortunately, it has not yet evolved to a point where it knows how to properly break-around longer lines as they often appear in source code files.
+The reader is kindly asked to open the source code files directly from [the GitHub repository where they are being kept](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group) if they wish to read them in detail.
+Towards that end, the appendix subheadings provide direct links to the files.
 
-TODO: remove below draft headings before handing the paper in!
+```{r, echo=FALSE}
+library(knitr)
+opts_chunk$set(tidy.opts = list(width.cutoff=60, indent=2), tidy=TRUE)
+```
 
-## 1.1 Data origin and possible intentions behind its compilation
-## 1.2 Data extraction and transformation into processable outer form
-## 1.3 Authors of the 18 works
-### 1.3.1 d. 728: Jarir ibn Atiyah (Yamamah, Damascus)
-### 1.3.2 d. 925: Muhammad ibn Zakariya al-Razi (Rey)
-### 1.3.3 d. 923: Al-Tabari (Amol-Baghdad)
-### 1.3.4 d. 971: Abū Ja'far al-Khāzin (Iran?)
-### 1.3.5 d. 1044: Al-Baghawi (?)
-### 1.3.6 d. 1058: Al-Mawardi (Basrah-Baghdad)
-### 1.3.7 d. 1142: Abu Hafs Umar an-Nasafi (Nakhshab-Samarqand)
-### 1.3.8 d. 1144: Al-Zamakhshari (Kwharezm-Mecca-Khwarezm)
-### 1.3.9 d. 1201: Ibn al-Jawzi (Baghdad)
-### 1.3.10 d. 1261: Ibn 'Abd as-Salam (Damascus-Egypt)
-### 1.3.11 d. 1273: Al-Qurtubi (Cortoba)
-### 1.3.12 d. 1286: Al-Baydawi (Shiraz-Tabriz)
-### 1.3.13 d. 1310: Shams al-Dīn al-Samarqandī (Samarqand)
-### 1.3.14 d. 1401: Ibn Arafa (Tunis)
-### 1.3.15 d. 1414: Fairuzabadi (Fars-Mekka)
-### 1.3.16 d. 1505: Al-Suyuti (Cairo)
-### 1.3.17 d. 1344: Abu Hayyan al-Gharnati (Spain-Cairo)
-### 1.3.18 d. 1373: Ibn Kathir (Bosra-Damascus)
-# 1.4 Conventional categorisation and inter-relationships of the authors
-# 2 Analysis
-# 2.1 Most frequent words (MFW), Zipf's law
-# 2.2 Stylometrics
-# 2.3 Topic Modelling results
-# 2.4 Congruences of observations with conventional views
-# 2.5 Notable differences to conventional views
-# 3 Conclusion
-# 3.1 Possible theses based on findings
-# 3.2 Discussion of necessary further work
+# I Script [`01_retrieval/download.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/download.r)
+
+```{r, code=readLines('../01_retrieval/download.r'), eval=FALSE}
+```
+
+# II Script [`01_retrieval/extract.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/extract.r)
+
+```{r, code=readLines('../01_retrieval/extract.r'), eval=FALSE}
+```
+
+# III Script [`01_retrieval/process.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/process.rb)
+
+```{ruby, code=readLines('../01_retrieval/process.rb'), eval=FALSE}
+```
+
+# IV Script [`01_retrieval/convert.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/convert.rb)
+
+```{ruby, code=readLines('../01_retrieval/convert.rb'), eval=FALSE}
+```
+
+# V Script [`02_analysis/wordcount_by_author.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_by_author.rb)
+
+```{ruby, code=readLines('../02_analysis/wordcount_by_author.rb'), eval=FALSE}
+```
+
+# VI Query [`02_analysis/wordcount_whole_corpus.sql`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_whole_corpus.sql)
+
+```{sql, code=readLines('../02_analysis/wordcount_whole_corpus.sql'), eval=FALSE}
+```

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
DMGizing the list of tafaseer.

@@
 
-# 2 The Tafasir
+# 2 The Tafāsīr
 
@@
 
-al-Bahr al-Muhit by Abu Hayyan
-al-Jami' li Ahkam al-Qur'an by al-Qurtubi
-al-Kashshaaf by al-Zamakhshari 
-al-Muharrar al-Wajiz fi Tafsir al-Kitaab al-'Aziz by Ibn Atiyyah
-Al-Nukat wal 'Uyuun by al-Mawardi
-Anwar al-Tanzil wa Asrar al-Ta’wil by al-Baydawi
-Bahr al-Uluum by al-Samarqandi
-Jami` al-bayan `an Ta'wil 'ay al-Qur'an by al-Tabari
-Lubab al-Ta'wil fi Ma'ani al-Tanzil by al-Khazin
-Ma’alm al-Tanzil by al-Baghawi
-Madarik al-Tanzil wa Haqa'iq al-Ta'wil by al-Nasafi
-Mafatih al-Ghayb by al-Razi
-Tafsir al-Jalalayn by al-Mahali and al-Suyuti
-Tafsir al-Qur'an by al-Fairuzabadi
-Tafsir al-Qur’an by Ibn Abd-al-Salam
-Tafsir al-Qur'an al-Azim by Ibn Kathir
-Zad al-Masir fi 'ilm al-Tafsir by Ibn al-Jawzi
+For reference, the following tafāsīr which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
+
+TODO: If anybody feels like properly capitalizing the titles again, I don't, rigt now.
+The uppercase letters can be looked up (and then copied and pasted) by clicking on the lowercase letters on https://en.wikipedia.org/wiki/DIN_31635.
+You could also try https://github.com/sixtyfive/de_dmg/blob/master/windows7810/de_dmg_amd64.msi if you have Windows, but it's quite old and I don't know if it'll still work (but it might).
+
+* *al-baḥr al-muḥīt* by *Abū Ḥayyān*
+* *al-ǧāmiʿ li-ʾaḥkām al-qurʾān* by *al-Qurṭubī*
+* *al-kaššāf* by *az-Zamaḫšarī*
+* *al-muḥarrar al-waǧīz fī tafsīr al-kitāb al-ʾazīz* by *Ibn ʿAṭīya*
+* *an-nukat wa-l-ʿuyūn* by *al-Māwardī*
+* *anwār at-tanzīl wa-ʾasrār at-taʾwīl* by *al-Bayḍāwī*
+* *baḥr al-ʿulūm* by *as-Samarqandī*
+* *ǧāmiʿ al-bayān fī tafsīr al-Qurʾān* by *aṭ-Ṭabarī*
+* *lubāb at-taʾwīl fī maʿānī at-tanzīl* by *al-Ḫāzin*
+* *maʿlam at-tanzīl* by *al-Baġawī*
+* *madārik at-tanzīl wa-ḥaqa'iq at-taʾwīl* by *an-Nasafī*
+* *mafātīḥ al-ġayb* by *ar-Rāzī*
+* *tafsīr al-ǧalālayn* by *al-Maḥallī* and *as-Suyūṭī*
+* *tafsīr al-qurʾān* by *al-Fayrūzābādī*
+* *tafsīr al-qurʾān* by *Ibn ʿAbdi-s-Salām*
+* *tafsīr al-qurʾān al-karīm* by *Ibn Kaṯīr*
+* *zād al-masīr fī ʿilm at-tafsīr* by *Ibnu-l-Ǧawzī*
 

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
Adding citations up until the end of the first paragraph that contains any. Substituting all typographical apostrophes with single quotation marks (this is, in the end, LaTeX!!!)

@@
 urlcolor: blue
+bibliography: Paper.bib
+csl: aethiopistische-forschungen.csl
 ---
@@
 * *baḥr al-ʿulūm* by *as-Samarqandī*
-* *ǧāmiʿ al-bayān fī tafsīr al-Qurʾān* by *aṭ-Ṭabarī*
+* *ǧāmiʿ al-bayān fī tafsīr al-qurʾān* by *aṭ-Ṭabarī*
 * *lubāb at-taʾwīl fī maʿānī at-tanzīl* by *al-Ḫāzin*
@@
 The unifying characteristic for the exegetes of the first cluster is their reputation as traditionalists.
-Al-Tabari saw his method of tafsir bil-mathur, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of bid’ah or heretical innovation (Bauer, 2013).
-Al-Baghawi emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muhammad or the sahaba, the companions of Muhammad (Robson, n.d.).
-Hanbali adherent Ibn al-Jawzi campaigned against the Shia in Iraq and authored a paean celebrating the end of Ismaili Fatimid rule in Egypt and the accession of a Sunni, Salah al-Din, to power (Mallett, n.d.).
-Ibn Atiyyah’s exegesis received praise from Ibn Taymiyyah, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (Salahi, 2002).
-The inclusion of Ibn Taymiyyah’s student Ibn Kathir can be attributed to either his conservative leanings—he penned a defense of armed Jihad against neighboring non-Muslim states (Laoust, n.d.)—or to his tafsir being, as some scholars have observed, a summarized version of al-Tabari’s (McAuliffe, 1991).
+Al-Tabari saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
+*Al-Baġawī* emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
+Hanbali adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of Ismaili Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
+*Ibn ʿAṭīya*'s exegesis received praise from *Ibn Taimīya*, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (@salahi2002).
+The inclusion of *Ibn Taimīya*'s student *Ibn Kaṯīr* can be attributed to either his conservative leanings—he penned a defense of armed Jihad against neighboring non-Muslim states (@ei_ibnkathir)—or to his *tafsīr* being, as some scholars have observed, a summarized version of *aṭ-Ṭabarī* (@mcauliffe1991).
+
+[^paean]: "a song, film, or piece of writing that praises someone or something very enthusiastically:" (Cambridge Dictionary of English)
 
@@
 For the second cluster, geography seems to be the unifying factor.
-Arabic grammarian and Mu’tazila partisan al-Zamakhshari (McAuliffe, 1991) differed from Hanafi jurist al-Nasafi on matters of doctrine (Poonawala, Wensinck & Heffening, n.d.) but they both lived in the Central Asian region known as Ma wara al-Nahr (Transoxiana) while the Shafi’i al-Baydawi lived in what is now Iran (Krauss-Sánchez, n.d.).
-Al-Baydawi’s exegesis Anwar al-tanzil wa asrar al-ta'wil has been labeled an amended version of al-Zamakhshari’s al-Kashshaaf, with Mu’tazila philosophy and other perceived heresies expunged from the text (McAuliffe, 1991).
+Arabic grammarian and Mu'tazila partisan al-Zamakhshari (McAuliffe, 1991) differed from Hanafi jurist al-Nasafi on matters of doctrine (Poonawala, Wensinck & Heffening, n.d.) but they both lived in the Central Asian region known as Ma wara al-Nahr (Transoxiana) while the Shafi'i al-Baydawi lived in what is now Iran (Krauss-Sánchez, n.d.).
+Al-Baydawi's exegesis Anwar al-tanzil wa asrar al-ta'wil has been labeled an amended version of al-Zamakhshari's al-Kashshaaf, with Mu'tazila philosophy and other perceived heresies expunged from the text (McAuliffe, 1991).
 This grouping may reflect a unique Central Asian outlook to the Quran and the addition of al-Baydawi may result from his reliance on the work of al-Zamakhshari.
@@
 Al-Razi lived in what is now Iran and Afghanistan (McAuliffe, 1991).
-In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of Mu’tazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta’wil or figurative reading in Quranic interpretation (Jaffer, 2015).
+In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of Mu'tazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta'wil or figurative reading in Quranic interpretation (Jaffer, 2015).
 Unfortunately, the inability to obtain word counts at the verse-level and therefore our inspection at the chapter-level may have adversely affected the quality of the groupings calculated by Gephi.
@@
 Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
-Amongst the four authors in this cluster three were from the school of Shafi’i and one from the school of Hanafi.
+Amongst the four authors in this cluster three were from the school of Shafi'i and one from the school of Hanafi.
 
@@
 During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
-The cities where al-mawari lived where known to be hubs of the Mu’tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu’tazaila jurisprudence) was in fact associated with the Shafi’i school of thought.
+The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the Shafi'i school of thought.
 He was later condemned for his Mu'tazila sympathies.
-Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of Shafi’i.
+Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of Shafi'i.
 Amongst the four jurist the Caliph favored Al-Mawardi and appointed chief imam.
@@
 Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and Al–Mawardi.
-During his time he was the leading authority in the Shafi’i Jurisprudence and most famous for his interpretations of Islamic legal principles.
+During his time he was the leading authority in the Shafi'i Jurisprudence and most famous for his interpretations of Islamic legal principles.
 Unlike al mawari ,Abd al-Salam was known to be defiant of customs he deemed “unsanctioned”.
@@
 Jalal al-Din al-Suyuti was born in Cario, Eygpt in the year 849AH (al-Suyuti, 2007) making his work the most recent amongst the cluster.
-Like most authors in the cluster he was a islamic jurist from the school of shafi’i.
-He was acknowledged as one of the more recent authority of the Shafi’i school whose degree of ijthad was accepted by most(Meri,2005).
+Like most authors in the cluster he was a islamic jurist from the school of shafi'i.
+He was acknowledged as one of the more recent authority of the Shafi'i school whose degree of ijthad was accepted by most(Meri,2005).
 Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
-Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the Hanafi school of jurisprudence and was tutored by a Sufi, though his work drew primarily from shafi’i school of thought.
-Al-Suyuti’s interest in the Hanafi jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
+Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the Hanafi school of jurisprudence and was tutored by a Sufi, though his work drew primarily from shafi'i school of thought.
+Al-Suyuti's interest in the Hanafi jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
 
@@
 In his work of the Quran al-samarqandi was known to relate the stories of sahabah and other hadiths from people not proven to be 100% reliable.
-He was also known for his lack of interest in the various methods of recitation (Qira’at).(“Liste..” 2002)  Unfortunately, due to lack of information on Al Samarqandi we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
+He was also known for his lack of interest in the various methods of recitation (Qira'at).(“Liste..” 2002) Unfortunately, due to lack of information on Al Samarqandi we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
 
@@
 
-# 4 References
-
-TODO: Move into Biblatex file, reference properly in the text, have it built automatically.
-
-"Al-Suyuti." Encyclopedia Britannica Online. May 16, 2007. Accessed December 1, 2016. https://www.britannica.com/biography/al-Suyuti.
-
-Bastian M., Heymann S., Jacomy M. (2009). Gephi: an open source software for exploring and manipulating networks. International AAAI Conference on Weblogs and Social Media
-
-Bauer, Karen (2013).
-“A Study of Introductions to Classical Works of Tafsir”,  in Karen Bauer (Ed) Aims, Methods and Contexts of Qur’anic Exegesis: (2nd/8th-9th/15th C.) (39-65).
-New York, NY: Oxford University Press.
-
-Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
-
-Fleisch, H., “al-Fīrūzābādī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
-
-Glazer, Sidney and Homerin, Th.
-Emil, “Abū Ḥayyān al-Gharnāṭī”, in: Encyclopaedia of Islam, THREE, Edited by: Kate Fleet, Gudrun Krämer, Denis Matringe, John Nawas, Everett Rowson.
-Retrieved from http://www.brillonline.com
-
-Jackson, Sherman A(1996). Islamic law and the state: the constitutional jurisprudence of Shihāb al-Dīn al-Qarāfī. Leiden: E.J. Brill, 1996.
-
-Jaffer, Tariq (2015). Razi: Master of Qur’anic Interpretation and Theological Reasoning. New York, NY: Oxford University Press.
-
-Krauss-Sánchez, Heidi R., “al-Baydāwī”, in: Encyclopedia of the Medieval Chronicle, Edited by: Graeme Dunphy, Cristian Bratu. First Published online 2016.  Retrieved
-From http://www.brillonline.com
-
-Laoust, H., “Ibn Kat̲h̲īr”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
-
-"Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.
-
-Mallett, Alex, “Ibn al-Jawzī”, in: Christian-Muslim Relations 600 - 1500, General Editor David Thomas. Retrieved From http://www.brillonline.com
-
-Meri, Josef W., ed. (2005). "Suyuti, Al-, 'Abd al-Rahman". Medieval Islamic Civilization: An Encyclopedia. Routledge. pp. 784–786.
-
-McAuliffe, Jane Dammen (1991). Qur’anic Christians: An Analysis of Classical and Modern Exegesis. New York, NY: Cambridge University Press.
-
-Poonawala, I., Wensinck, A.J.
-and Heffening, W., “al-Nasafī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P.
-Bearman, Th.
-Bianquis, C.E.
-Bosworth, E.
-van Donzel, W.P.
-Heinrichs.
-Retrieved from http://www.brillonline.com
-
-Robson, J., “al-Bag̲h̲awī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://brillonline.com
-
-Salahi, Adil (2002, October 14). Scholar of Renown: Ibn Atiyyah. Arab News. Retrieved from http://www.arabnews.com
-
-Salahi , Adil. "Izz Al-Din ibn Abd Al-Salam." Izz Al-Din ibn Abd Al-Salam | Muslim Heritage. Accessed December 1, 2016. http://www.muslimheritage.com/article/izz-al-din-ibn-abd-al-salam.
-
-Sharif , M M. "Al-MĀWARDĪ." Encyclopaedia of Islam, Second Edition1, no. 3 (August 8, 2002). Accessed December 1, 2016. doi:10.1163/1573-3912_islam_com_0713.
-
-Wheeler, Brannon M. Prophets in the Quran: an introduction to the Quran and Muslim exegesis. London: Continuum, 2002.
-pg 337
-
-Zahoor, A., Dr. "Al-Mawardi, 972-1058 C.E." Al-Mawardi, 972-1058 C.E. January 15, 1998. Accessed December 1, 2016. http://www.unhas.ac.id/rhiza/arsip/saintis/mawardi.html.
-
 # Appendix
 
-Note: as this document was prepared using the `rmarkdown` package, consequently `knitr`'s built-in devices are being used to include our source code in the below appendices for reference.
+Note on source code formatting: as this document was prepared using the `rmarkdown` package, consequently `knitr`'s built-in devices are being used to include our source code in the below appendices for reference.
 Unfortunately, it has not yet evolved to a point where it knows how to properly break-around longer lines as they often appear in source code files.
@@
 Towards that end, the appendix subheadings provide direct links to the files.
+
+Note on placement of appendix and references: another limitation of using Rmarkdown for scientific documents is the placement of references at the end of the document and nowhere else.
+This can only be worked around by use of a modified template file as described in [the Rmarkdown documentation's comment section](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
+Unfortunately, time constraints didn't allow creation of such a template for this document.
 
@@
 ```
+# 4 References
+
+TODO: Keep moving them into Biblatex file, keep referencing properly in the text.
+
+"Al-Suyuti." Encyclopedia Britannica Online. May 16, 2007. Accessed December 1, 2016. https://www.britannica.com/biography/al-Suyuti.
+
+Bastian M., Heymann S., Jacomy M. (2009). Gephi: an open source software for exploring and manipulating networks. International AAAI Conference on Weblogs and Social Media
+
+Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
+
+Fleisch, H., “al-Fīrūzābādī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
+
+Glazer, Sidney and Homerin, Th.
+Emil, “Abū Ḥayyān al-Gharnāṭī”, in: Encyclopaedia of Islam, THREE, Edited by: Kate Fleet, Gudrun Krämer, Denis Matringe, John Nawas, Everett Rowson.
+Retrieved from http://www.brillonline.com
+
+Jackson, Sherman A(1996). Islamic law and the state: the constitutional jurisprudence of Shihāb al-Dīn al-Qarāfī. Leiden: E.J. Brill, 1996.
+
+Jaffer, Tariq (2015). Razi: Master of Qur'anic Interpretation and Theological Reasoning. New York, NY: Oxford University Press.
+
+Krauss-Sánchez, Heidi R., “al-Baydāwī”, in: Encyclopedia of the Medieval Chronicle, Edited by: Graeme Dunphy, Cristian Bratu. First Published online 2016. Retrieved
+From http://www.brillonline.com
+
+"Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.
+
+Meri, Josef W., ed. (2005). "Suyuti, Al-, 'Abd al-Rahman". Medieval Islamic Civilization: An Encyclopedia. Routledge. pp. 784–786.
+
+Poonawala, I., Wensinck, A.J.
+and Heffening, W., “al-Nasafī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P.
+Bearman, Th.
+Bianquis, C.E.
+Bosworth, E.
+van Donzel, W.P.
+Heinrichs.
+Retrieved from http://www.brillonline.com
+
+Sharif , M M. "Al-MĀWARDĪ." Encyclopaedia of Islam, Second Edition1, no. 3 (August 8, 2002). Accessed December 1, 2016. doi:10.1163/1573-3912_islam_com_0713.
+
+Wheeler, Brannon M. Prophets in the Quran: an introduction to the Quran and Muslim exegesis. London: Continuum, 2002.
+pg 337
+
+Zahoor, A., Dr. "Al-Mawardi, 972-1058 C.E." Al-Mawardi, 972-1058 C.E. January 15, 1998. Accessed December 1, 2016. http://www.unhas.ac.id/rhiza/arsip/saintis/mawardi.html.

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
Removing obsolete comment
More transliterations, more citations, also adding a short paragraph on transliteration choices.

@@
 
-# 2 The Tafāsīr
+1.1 A note on transliteration
+
+The transliteration system used is that of the [German Oriental Society](http://www.dmg-web.de/)[^dmg].
+We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names), but for reasons stylistic reasons or other case-by-case considerations there can be slight inconsistencies for which we ask the reader's digression (i.e., vowelisation was sometimes added where it helps the flow of pronounciation).
+With regards to diphtong phonemes we have opted towards the variant employing the combination of one consonantal and one vowel representation which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
+Proper names were translterated starting with capital letters only at the beginning of a sentence or if they are a person's or a place's name.
+Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if part of a group of other Arabic words.
+
+[^dmg]: *Deutsche Morgenländische Gesellschaft* in the original.
+A copy of the latest transliteration rules anno 1969 is available from [http://www.dmg-web.de/pdf/Denkschrift.pdf](http://www.dmg-web.de/pdf/Denkschrift.pdf).
+
+[^englishwords]: Such as Quran, Sunni, Shia, Fatimid, etc.
+
+# 2 The tafāsīr
 
@@
 
-1. Green: *Ibnu-l-Ǧawzī* (d. 597 AH),, *aṭ-Ṭabarī* (d. 310 AH), *Ibn Kaṯīr* (d. 774 AH), *Ibn ʿAṭīya* (d. 546 AH), and *al-Baġawī* (d. 516 AH)
+1. Green: *Ibnu-l-Ǧawzī* (d. 597 AH), *aṭ-Ṭabarī* (d. 310 AH), *Ibn Kaṯīr* (d. 774 AH), *Ibn ʿAṭīya* (d. 546 AH), and *al-Baġawī* (d. 516 AH)
 2. Blue: *az-Zamaḫšarī* (d. 538 AH), *al-Bayḍāwī* (d. 685 AH), and *an-Nasafī* (d. 710 AH)
@@
 
-TODO: DMGize, mark citations
-
 The unifying characteristic for the exegetes of the first cluster is their reputation as traditionalists.
-Al-Tabari saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
+*Aṭ-Ṭabarī* saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
 *Al-Baġawī* emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
-Hanbali adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of Ismaili Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
+*Ḥanbalī* adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of *ismaʿīlī* Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
 *Ibn ʿAṭīya*'s exegesis received praise from *Ibn Taimīya*, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (@salahi2002).
@@
 
-TODO: DMGize, mark citations
-
 For the second cluster, geography seems to be the unifying factor.
-Arabic grammarian and Mu'tazila partisan al-Zamakhshari (McAuliffe, 1991) differed from Hanafi jurist al-Nasafi on matters of doctrine (Poonawala, Wensinck & Heffening, n.d.) but they both lived in the Central Asian region known as Ma wara al-Nahr (Transoxiana) while the Shafi'i al-Baydawi lived in what is now Iran (Krauss-Sánchez, n.d.).
-Al-Baydawi's exegesis Anwar al-tanzil wa asrar al-ta'wil has been labeled an amended version of al-Zamakhshari's al-Kashshaaf, with Mu'tazila philosophy and other perceived heresies expunged from the text (McAuliffe, 1991).
-This grouping may reflect a unique Central Asian outlook to the Quran and the addition of al-Baydawi may result from his reliance on the work of al-Zamakhshari.
+Arabic grammarian and *muʿtazila* partisan *az-Zamaḫšarī* (@mcauliffe1991) differed from ḥanafī jurist *an-Nasafī* on matters of doctrine (@ei_annasafi) but they both lived in the Central Asian region known as *mā warāʾu-n-nahr* (Transoxiana) while the šāfiʿī *al-Bayḍāwī* lived in what is now Iran (@emc_albaydawi).
+*Al-Bayḍāwī*'s exegesis *anwār at-tanzīl wa-ʾasrār at-taʾwīl* has been labeled an amended version of *az-Zamaḫšarī*'s *al-kaššāf*, with *muʿtazila* philosophy and other perceived heresies expunged from the text (@mcauliffe1991).
+This grouping may reflect a unique Central Asian outlook to the Quran and the addition of *al-Bayḍāwī* may result from his reliance on the work of *az-Zamaḫšarī*.
 
@@
 If there is a latent, unifying factor to the mufasiroon of the third cluster, it is not immediately apparent to us.
-The exegetes were not contemporaneous to one another with al-Razi preceding al-Fairuzabadi by two centuries.
+The exegetes were not contemporaneous to one another with al-Razi preceding *al-Fayrūzābādī* by two centuries.
 Geography certainly did not connect the writers.
 Abu Hayyan (Glazer & Homerin, n.d.) and al-Qurtubi were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
-Al-Khazin lived in Syria which also was briefly the home of Persian-born al-Fairuzabadi who also spent his life in Jerusalem, Mecca, and Yemen (Fleisch, n.d.).
-Al-Razi lived in what is now Iran and Afghanistan (McAuliffe, 1991).
-In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of Mu'tazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta'wil or figurative reading in Quranic interpretation (Jaffer, 2015).
+Al-Khazin lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (Fleisch, n.d.).
+Al-Razi lived in what is now Iran and Afghanistan (@mcauliffe1991).
+In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of muʿtazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta'wil or figurative reading in Quranic interpretation (Jaffer, 2015).
 Unfortunately, the inability to obtain word counts at the verse-level and therefore our inspection at the chapter-level may have adversely affected the quality of the groupings calculated by Gephi.
@@
 Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
-Amongst the four authors in this cluster three were from the school of Shafi'i and one from the school of Hanafi.
+Amongst the four authors in this cluster three were from the school of šāfiʿī and one from the school of ḥanafī.
 
@@
 During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
-The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the Shafi'i school of thought.
-He was later condemned for his Mu'tazila sympathies.
-Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of Shafi'i.
+The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the šāfiʿī school of thought.
+He was later condemned for his muʿtazila sympathies.
+Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of šāfiʿī.
 Amongst the four jurist the Caliph favored Al-Mawardi and appointed chief imam.
@@
 Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and Al–Mawardi.
-During his time he was the leading authority in the Shafi'i Jurisprudence and most famous for his interpretations of Islamic legal principles.
+During his time he was the leading authority in the šāfiʿī Jurisprudence and most famous for his interpretations of Islamic legal principles.
 Unlike al mawari ,Abd al-Salam was known to be defiant of customs he deemed “unsanctioned”.
@@
 Jalal al-Din al-Suyuti was born in Cario, Eygpt in the year 849AH (al-Suyuti, 2007) making his work the most recent amongst the cluster.
-Like most authors in the cluster he was a islamic jurist from the school of shafi'i.
-He was acknowledged as one of the more recent authority of the Shafi'i school whose degree of ijthad was accepted by most(Meri,2005).
+Like most authors in the cluster he was a islamic jurist from the school of šāfiʿī.
+He was acknowledged as one of the more recent authority of the šāfiʿī school whose degree of ijthad was accepted by most(Meri,2005).
 Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
-Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the Hanafi school of jurisprudence and was tutored by a Sufi, though his work drew primarily from shafi'i school of thought.
-Al-Suyuti's interest in the Hanafi jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
+Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the ḥanafī school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.
+Al-Suyuti's interest in the ḥanafī jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
 
@@
 
-Abu al-Layth al-Samarqandi author of Bahr Ul ‘Ulum was the single author in the cluster from the school of Hanafi.
+Abu al-Layth al-Samarqandi author of Bahr Ul ‘Ulum was the single author in the cluster from the school of ḥanafī.
 Apart from his jurisprudence another outlying factor for al-Samaraqandi was his geographical location and time period.
@@
 
-Krauss-Sánchez, Heidi R., “al-Baydāwī”, in: Encyclopedia of the Medieval Chronicle, Edited by: Graeme Dunphy, Cristian Bratu. First Published online 2016. Retrieved
-From http://www.brillonline.com
-
 "Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
Another paragraph transliterated; correcting some chapter heading levels.

@@
 
-1.1 A note on transliteration
+## 1.1 A note on transliteration
 
@@
 
-TODO: DMGize
-
-For reference, the following tafāsīr which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
-
-TODO: If anybody feels like properly capitalizing the titles again, I don't, rigt now.
-The uppercase letters can be looked up (and then copied and pasted) by clicking on the lowercase letters on https://en.wikipedia.org/wiki/DIN_31635.
-You could also try https://github.com/sixtyfive/de_dmg/blob/master/windows7810/de_dmg_amd64.msi if you have Windows, but it's quite old and I don't know if it'll still work (but it might).
+For reference, the following *tafāsīr* which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
 
@@
 
-[^paean]: "a song, film, or piece of writing that praises someone or something very enthusiastically:" (Cambridge Dictionary of English)
+[^paean]: "[A] song, film, or piece of writing that praises someone or something very enthusiastically:" (Cambridge Dictionary of English)
 
 For the second cluster, geography seems to be the unifying factor.
-Arabic grammarian and *muʿtazila* partisan *az-Zamaḫšarī* (@mcauliffe1991) differed from ḥanafī jurist *an-Nasafī* on matters of doctrine (@ei_annasafi) but they both lived in the Central Asian region known as *mā warāʾu-n-nahr* (Transoxiana) while the šāfiʿī *al-Bayḍāwī* lived in what is now Iran (@emc_albaydawi).
+Arabic grammarian and *muʿtazila* partisan *az-Zamaḫšarī* (@mcauliffe1991) differed from *ḥanafī* jurist *an-Nasafī* on matters of doctrine (@ei_annasafi) but they both lived in the Central Asian region known as *mā warāʾu-n-nahr* (Transoxiana) while the šāfiʿī *al-Bayḍāwī* lived in what is now Iran (@emc_albaydawi).
 *Al-Bayḍāwī*'s exegesis *anwār at-tanzīl wa-ʾasrār at-taʾwīl* has been labeled an amended version of *az-Zamaḫšarī*'s *al-kaššāf*, with *muʿtazila* philosophy and other perceived heresies expunged from the text (@mcauliffe1991).
@@
 
-TODO: DMGize, mark citations
-
-If there is a latent, unifying factor to the mufasiroon of the third cluster, it is not immediately apparent to us.
-The exegetes were not contemporaneous to one another with al-Razi preceding *al-Fayrūzābādī* by two centuries.
+If there is a latent, unifying factor to the *mufassirūn* of the third cluster, it is not immediately apparent to us.
+The exegetes were not contemporaneous to one another with *ar-Rāzī* preceding *al-Fayrūzābādī* by two centuries.
 Geography certainly did not connect the writers.
-Abu Hayyan (Glazer & Homerin, n.d.) and al-Qurtubi were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
-Al-Khazin lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (Fleisch, n.d.).
-Al-Razi lived in what is now Iran and Afghanistan (@mcauliffe1991).
-In terms of doctrinal leanings, Abu Hayyan was a traditionalist and admirer of Ibn Taymiyyah (Glazer & Homerin, n.d.) while al-Razi, though ostensibly a critic of muʿtazila theology, is seen to have incorporated heterodox tenets emphasizing reason and ta'wil or figurative reading in Quranic interpretation (Jaffer, 2015).
-Unfortunately, the inability to obtain word counts at the verse-level and therefore our inspection at the chapter-level may have adversely affected the quality of the groupings calculated by Gephi.
+*Abū Ḥayyān* (@ei_abuhayyan) and *al-Qurṭubī* were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
+Al-Khazin lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (@ei_alfiruzabadi).
+*ar-Rāzī* lived in what is now Iran and Afghanistan (@mcauliffe1991).
+In terms of doctrinal leanings, *Abū Ḥayyān* was a traditionalist and admirer of *Ibn Taimīya* (@ei_abuhayyan) while *ar-Rāzī*, though ostensibly a critic of *muʿtazila* theology, is seen to have incorporated heterodox tenets emphasizing reason and *taʾwīl* or figurative reading in Quranic interpretation (Jaffer, 2015).
+Unfortunately, the inability to obtain reliable word counts at the verse-level (and therefore our inspection at the chapter-level) may have adversely affected the quality of the groupings calculated by Gephi.
 
@@
 The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the šāfiʿī school of thought.
-He was later condemned for his muʿtazila sympathies.
+He was later condemned for his *muʿtazila* sympathies.
 Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of šāfiʿī.
@@
 Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
-Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the ḥanafī school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.
-Al-Suyuti's interest in the ḥanafī jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
+Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.
+Al-Suyuti's interest in the *ḥanafī* jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
 
@@
 
-# I Script [`01_retrieval/download.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/download.r)
+## I Script [`01_retrieval/download.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/download.r)
 
@@
 
-# II Script [`01_retrieval/extract.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/extract.r)
+## II Script [`01_retrieval/extract.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/extract.r)
 
@@
 
-# III Script [`01_retrieval/process.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/process.rb)
+## III Script [`01_retrieval/process.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/process.rb)
 
@@
 
-# IV Script [`01_retrieval/convert.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/convert.rb)
+## IV Script [`01_retrieval/convert.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/convert.rb)
 
@@
 
-# V Script [`02_analysis/wordcount_by_author.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_by_author.rb)
+## V Script [`02_analysis/wordcount_by_author.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_by_author.rb)
 
@@
 
-# VI Query [`02_analysis/wordcount_whole_corpus.sql`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_whole_corpus.sql)
+## VI Query [`02_analysis/wordcount_whole_corpus.sql`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_whole_corpus.sql)
 
@@
 Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
-
-Fleisch, H., “al-Fīrūzābādī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P. Bearman, Th. Bianquis, C.E. Bosworth, E. van Donzel, W.P. Heinrichs. Retrieved From http://www.brillonline.com
-
-Glazer, Sidney and Homerin, Th.
-Emil, “Abū Ḥayyān al-Gharnāṭī”, in: Encyclopaedia of Islam, THREE, Edited by: Kate Fleet, Gudrun Krämer, Denis Matringe, John Nawas, Everett Rowson.
-Retrieved from http://www.brillonline.com
 

### 2016-12-19 tafaseer_group/03_results/Paper.Rmd
On a suspicion that this might be Thom's preferred style...

@@
 csl: aethiopistische-forschungen.csl
+header-includes:
+  - \setlength\parindent{24pt}\setlength{\parskip}{0.0pt plus 1.0pt}
 ---

### 2016-12-20 tafaseer_group/03_results/appendix.rmd
Moving things around wildly. Sorry, too tired for detailled breakdown.

--- 2016-12-19 tafaseer_group/03_results/Paper.Rmd
@@
----
-title: Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th
- Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
-subtitle: Universities of Leipzig and Maryland
-author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
-date: "`r format(Sys.time(), '%d %B %Y')`"
-tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
-abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran).
-Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
-output: pdf_document
-toc: no
-fontsize: 12pt
-geometry: margin=1.5in
-lang: en
-documentclass: article
-latex_engine: xelatex
-urlcolor: blue
-bibliography: Paper.bib
-csl: aethiopistische-forschungen.csl
----
-
-# 1 Introduction
-
-How has Islamic interpretation of the Quran changed over time?
-Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time?
-Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another?
-Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration?
-To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format.
-
-## 1.1 A note on transliteration
-
-The transliteration system used is that of the [German Oriental Society](http://www.dmg-web.de/)[^dmg].
-We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names), but for reasons stylistic reasons or other case-by-case considerations there can be slight inconsistencies for which we ask the reader's digression (i.e., vowelisation was sometimes added where it helps the flow of pronounciation).
-With regards to diphtong phonemes we have opted towards the variant employing the combination of one consonantal and one vowel representation which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
-Proper names were translterated starting with capital letters only at the beginning of a sentence or if they are a person's or a place's name.
-Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if part of a group of other Arabic words.
-
-[^dmg]: *Deutsche Morgenländische Gesellschaft* in the original.
-A copy of the latest transliteration rules anno 1969 is available from [http://www.dmg-web.de/pdf/Denkschrift.pdf](http://www.dmg-web.de/pdf/Denkschrift.pdf).
-
-[^englishwords]: Such as Quran, Sunni, Shia, Fatimid, etc.
-
-# 2 The tafāsīr
-
-For reference, the following *tafāsīr* which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
-
-* *al-baḥr al-muḥīt* by *Abū Ḥayyān*
-* *al-ǧāmiʿ li-ʾaḥkām al-qurʾān* by *al-Qurṭubī*
-* *al-kaššāf* by *az-Zamaḫšarī*
-* *al-muḥarrar al-waǧīz fī tafsīr al-kitāb al-ʾazīz* by *Ibn ʿAṭīya*
-* *an-nukat wa-l-ʿuyūn* by *al-Māwardī*
-* *anwār at-tanzīl wa-ʾasrār at-taʾwīl* by *al-Bayḍāwī*
-* *baḥr al-ʿulūm* by *as-Samarqandī*
-* *ǧāmiʿ al-bayān fī tafsīr al-qurʾān* by *aṭ-Ṭabarī*
-* *lubāb at-taʾwīl fī maʿānī at-tanzīl* by *al-Ḫāzin*
-* *maʿlam at-tanzīl* by *al-Baġawī*
-* *madārik at-tanzīl wa-ḥaqa'iq at-taʾwīl* by *an-Nasafī*
-* *mafātīḥ al-ġayb* by *ar-Rāzī*
-* *tafsīr al-ǧalālayn* by *al-Maḥallī* and *as-Suyūṭī*
-* *tafsīr al-qurʾān* by *al-Fayrūzābādī*
-* *tafsīr al-qurʾān* by *Ibn ʿAbdi-s-Salām*
-* *tafsīr al-qurʾān al-karīm* by *Ibn Kaṯīr*
-* *zād al-masīr fī ʿilm at-tafsīr* by *Ibnu-l-Ǧawzī*
-
-# 2 The corpus
-
-As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
-The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*.
-This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on.
-The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts originating from various traditions, sects, and schools of jurisprudence.
-That desired breadth has yet to be achieved.
-The website currently has seventeen complete tafāsīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.
-
-# 3 Methodology
-
-Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the tafsir that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*.
-It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*.
-Importance might not necessarily mean that the *mufassir* had an increased affinity for the values or instructions espoused in the verse.
-A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the Muslim layman and therefore devoted more writing to explication and contextualizing.
-
-When we sorted the verses from most written about to least, we observed some suspicious patterns.
-Consecutive verses were appearing next to one another on the list and they had identical word counts.
-When we inspected the files in our corpus, we found that there were duplicate chunks of text.
-The problem was that most of the writers alternated between writing about singles verses and writing about groups of consecutive verses that dealt with a single narrative or theme.
-If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website.
-When the script to download the tafāsīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse.
-Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem.
-Of the 87 *tafsīr* works listed on the website, 69 turned out to be completely empty and one author, *Ibn ʿArafa*, only provided commentary on *sūratān*.
-Both were removed from the corpus used for analysis, which consequently consists of 17 works comprising $i_{total}=16444304$ words.
-
-We ran a script that looked for duplicate texts and removed any repeated segments.
-Since we were not able to get word counts for specific verses, we decided to focus on the *sūra* or chapters of the Quran.
-There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest.
-We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting.
-We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
-The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.
-
-## 3.1 The Results
-
-![Gephi social network analysis result](../02_analysis/data_manual/gephi/mufasirooncomparison.png)
-
-The data as described so far was run through the Gephi social network analysis program. The algorithm calculated four distinct groups, represented as colors in figure 1. They are as follows:
-
-1. Green: *Ibnu-l-Ǧawzī* (d. 597 AH), *aṭ-Ṭabarī* (d. 310 AH), *Ibn Kaṯīr* (d. 774 AH), *Ibn ʿAṭīya* (d. 546 AH), and *al-Baġawī* (d. 516 AH)
-2. Blue: *az-Zamaḫšarī* (d. 538 AH), *al-Bayḍāwī* (d. 685 AH), and *an-Nasafī* (d. 710 AH)
-3. Purple: *ar-Rāzī* (d. 606 AH), *al-Fayrūzābādī* (d. 817 AH), *al-Qurṭubī* (d. 671 AH), *al-Ḫāzin* (d. 741 AH), and *Abū Ḥayyān* (d. 754 AH)
-4. Orange: *al-Maḥallī* (d. 864 AH) and *as-Suyūṭī* (d. 911 AH), *as-Samarqandī* (d. 375 AH), *al-Māwardī* (d. 450 AH), and *Ibn ʿAbdi-s-Salām* (d. 660 AH)
-
-The unifying characteristic for the exegetes of the first cluster is their reputation as traditionalists.
-*Aṭ-Ṭabarī* saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
-*Al-Baġawī* emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
-*Ḥanbalī* adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of *ismaʿīlī* Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
-*Ibn ʿAṭīya*'s exegesis received praise from *Ibn Taimīya*, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (@salahi2002).
-The inclusion of *Ibn Taimīya*'s student *Ibn Kaṯīr* can be attributed to either his conservative leanings—he penned a defense of armed Jihad against neighboring non-Muslim states (@ei_ibnkathir)—or to his *tafsīr* being, as some scholars have observed, a summarized version of *aṭ-Ṭabarī* (@mcauliffe1991).
-
-[^paean]: "[A] song, film, or piece of writing that praises someone or something very enthusiastically:" (Cambridge Dictionary of English)
-
-For the second cluster, geography seems to be the unifying factor.
-Arabic grammarian and *muʿtazila* partisan *az-Zamaḫšarī* (@mcauliffe1991) differed from *ḥanafī* jurist *an-Nasafī* on matters of doctrine (@ei_annasafi) but they both lived in the Central Asian region known as *mā warāʾu-n-nahr* (Transoxiana) while the šāfiʿī *al-Bayḍāwī* lived in what is now Iran (@emc_albaydawi).
-*Al-Bayḍāwī*'s exegesis *anwār at-tanzīl wa-ʾasrār at-taʾwīl* has been labeled an amended version of *az-Zamaḫšarī*'s *al-kaššāf*, with *muʿtazila* philosophy and other perceived heresies expunged from the text (@mcauliffe1991).
-This grouping may reflect a unique Central Asian outlook to the Quran and the addition of *al-Bayḍāwī* may result from his reliance on the work of *az-Zamaḫšarī*.
-
-If there is a latent, unifying factor to the *mufassirūn* of the third cluster, it is not immediately apparent to us.
-The exegetes were not contemporaneous to one another with *ar-Rāzī* preceding *al-Fayrūzābādī* by two centuries.
-Geography certainly did not connect the writers.
-*Abū Ḥayyān* (@ei_abuhayyan) and *al-Qurṭubī* were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
-Al-Khazin lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (@ei_alfiruzabadi).
-*ar-Rāzī* lived in what is now Iran and Afghanistan (@mcauliffe1991).
-In terms of doctrinal leanings, *Abū Ḥayyān* was a traditionalist and admirer of *Ibn Taimīya* (@ei_abuhayyan) while *ar-Rāzī*, though ostensibly a critic of *muʿtazila* theology, is seen to have incorporated heterodox tenets emphasizing reason and *taʾwīl* or figurative reading in Quranic interpretation (Jaffer, 2015).
-Unfortunately, the inability to obtain reliable word counts at the verse-level (and therefore our inspection at the chapter-level) may have adversely affected the quality of the groupings calculated by Gephi.
-
-TODO: DMGize, mark citations
-
-The last cluster of our analysis resulted in a predictable grouping of exegetes.
-The primary characteristic that unified these authors was their choice of school of jurisprudence.
-Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
-Amongst the four authors in this cluster three were from the school of šāfiʿī and one from the school of ḥanafī.
-
-TODO: DMGize, mark citations
-
-Al–Mawardi was an Islamic jurist born in Basra, Iraq during 364AH (Sharif, 2002).
-During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
-The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the šāfiʿī school of thought.
-He was later condemned for his *muʿtazila* sympathies.
-Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of šāfiʿī.
-Amongst the four jurist the Caliph favored Al-Mawardi and appointed chief imam.
-(Sharif, 2002) Along with the school of jurisprudence a common factor amongst most of the authors was their interest or relation in Islamic law.
-
-TODO: DMGize, mark citations
-
-Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and Al–Mawardi.
-During his time he was the leading authority in the šāfiʿī Jurisprudence and most famous for his interpretations of Islamic legal principles.
-Unlike al mawari ,Abd al-Salam was known to be defiant of customs he deemed “unsanctioned”.
-He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus As-Salih Ismail.(Jackson, 1996) This condemning led to his imprisonment and eventual emigration to Cairo, Egypt.
-In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt.
-(Salahi) Like Al-Mawardi, Al- Salam was a world renowned scholar of fatwas.
-Al-salam was so respected, islamic jurist like al-Hafiz al-Mundhiri stopped giving fatwas stating "It does not behove any jurist to give a fatwa where Izz al-Din(Ibn 'Abd al-Salam) happens to be present."(Salahi) Both Ibn 'Abd al-Salam and Al-Mawardi were highly respected scholars of their time especially in regards to islamic law.
-Both authors were advisors to their respected islamic governments of their time,(Jackson, 1996) another factor which may have attributed to the groups of these authors in the same cluster.
-
-TODO: DMGize, mark citations
-
-Jalal al-Din al-Suyuti was born in Cario, Eygpt in the year 849AH (al-Suyuti, 2007) making his work the most recent amongst the cluster.
-Like most authors in the cluster he was a islamic jurist from the school of šāfiʿī.
-He was acknowledged as one of the more recent authority of the šāfiʿī school whose degree of ijthad was accepted by most(Meri,2005).
-Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
-Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.
-Al-Suyuti's interest in the *ḥanafī* jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
-
-TODO: DMGize, mark citations
-
-Abu al-Layth al-Samarqandi author of Bahr Ul ‘Ulum was the single author in the cluster from the school of ḥanafī.
-Apart from his jurisprudence another outlying factor for al-Samaraqandi was his geographical location and time period.
-He was born in Afghanistan during 373AH making him the oldest exegete in this cluster.
-(wheeler, 2002) Since his worked dated back so far we were unable to find much information in regards to his lifestyle or any other factors that may have attributed to his placing in this cluster although, however we were able to compile a few specific features of his exegesis.
-In his work of the Quran al-samarqandi was known to relate the stories of sahabah and other hadiths from people not proven to be 100% reliable.
-He was also known for his lack of interest in the various methods of recitation (Qira'at).(“Liste..” 2002) Unfortunately, due to lack of information on Al Samarqandi we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
-
-TODO: DMGize, mark citations
-
-From the results of the study, we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of the paper (chronology, geography, dogma).
-However, we believe that examination of surah and ayah preference from Quranic exegetes deserves further exploration.
-
 # Appendix
-
-Note on source code formatting: as this document was prepared using the `rmarkdown` package, consequently `knitr`'s built-in devices are being used to include our source code in the below appendices for reference.
-Unfortunately, it has not yet evolved to a point where it knows how to properly break-around longer lines as they often appear in source code files.
-The reader is kindly asked to open the source code files directly from [the GitHub repository where they are being kept](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group) if they wish to read them in detail.
-Towards that end, the appendix subheadings provide direct links to the files.
-
-Note on placement of appendix and references: another limitation of using Rmarkdown for scientific documents is the placement of references at the end of the document and nowhere else.
-This can only be worked around by use of a modified template file as described in [the Rmarkdown documentation's comment section](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
-Unfortunately, time constraints didn't allow creation of such a template for this document.
 
@@
 ```
-# 4 References
-
-TODO: Keep moving them into Biblatex file, keep referencing properly in the text.
-
-"Al-Suyuti." Encyclopedia Britannica Online. May 16, 2007. Accessed December 1, 2016. https://www.britannica.com/biography/al-Suyuti.
-
-Bastian M., Heymann S., Jacomy M. (2009). Gephi: an open source software for exploring and manipulating networks. International AAAI Conference on Weblogs and Social Media
-
-Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
-
-Jackson, Sherman A(1996). Islamic law and the state: the constitutional jurisprudence of Shihāb al-Dīn al-Qarāfī. Leiden: E.J. Brill, 1996.
-
-Jaffer, Tariq (2015). Razi: Master of Qur'anic Interpretation and Theological Reasoning. New York, NY: Oxford University Press.
-
-"Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.
-
-Meri, Josef W., ed. (2005). "Suyuti, Al-, 'Abd al-Rahman". Medieval Islamic Civilization: An Encyclopedia. Routledge. pp. 784–786.
-
-Poonawala, I., Wensinck, A.J.
-and Heffening, W., “al-Nasafī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P.
-Bearman, Th.
-Bianquis, C.E.
-Bosworth, E.
-van Donzel, W.P.
-Heinrichs.
-Retrieved from http://www.brillonline.com
-
-Sharif , M M. "Al-MĀWARDĪ." Encyclopaedia of Islam, Second Edition1, no. 3 (August 8, 2002). Accessed December 1, 2016. doi:10.1163/1573-3912_islam_com_0713.
-
-Wheeler, Brannon M. Prophets in the Quran: an introduction to the Quran and Muslim exegesis. London: Continuum, 2002.
-pg 337
-
-Zahoor, A., Dr. "Al-Mawardi, 972-1058 C.E." Al-Mawardi, 972-1058 C.E. January 15, 1998. Accessed December 1, 2016. http://www.unhas.ac.id/rhiza/arsip/saintis/mawardi.html.

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Moving things around wildly. Sorry, too tired for detailled breakdown.

--- 2016-12-19 tafaseer_group/03_results/Paper.Rmd
@@
 abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran).
-Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
-output: pdf_document
+Through network analysis, it was possible to draw first conclusions about the acquired data.
 toc: no
-fontsize: 12pt
-geometry: margin=1.5in
+fontsize: 11pt
 lang: en
 documentclass: article
-latex_engine: xelatex
+geometry: margin=1.25in
 urlcolor: blue
-bibliography: Paper.bib
+bibliography: paper.bib
 csl: aethiopistische-forschungen.csl
 ---
+
+***
 
@@
 
-The transliteration system used is that of the [German Oriental Society](http://www.dmg-web.de/)[^dmg].
-We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names), but for reasons stylistic reasons or other case-by-case considerations there can be slight inconsistencies for which we ask the reader's digression (i.e., vowelisation was sometimes added where it helps the flow of pronounciation).
+The transliteration system used is that of the German Oriental Society[^dmg_url].
+We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names); for the inconsistencies that remain (i.e., vowelisation was sometimes added where it helps the flow of pronounciation) we ask the reader's digression.
 With regards to diphtong phonemes we have opted towards the variant employing the combination of one consonantal and one vowel representation which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
@@
 Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if part of a group of other Arabic words.
+
+[^dmg_url]: [http://www.dmg-web.de/](http://www.dmg-web.de/)
 
@@
 
-# 2 The tafāsīr
+## 1.2 A technical note regarding this document
 
-For reference, the following *tafāsīr* which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
+The present document was prepared using the `rmarkdown` package and consequently `knitr`'s built-in devices are being used to include the source code relevant to this study in the appendix.
+Unfortunately, the underlying libraries have not yet evolved to a point where they knows how to properly break-around longer lines as they often appear in source code files.
+The reader is kindly asked to open the source code files directly from the GitHub repository where they are being kept[^github] if she wishes to read them in detail.
+Towards that end, the appendix subheadings provide direct links to the respective files displayed beneath them.
+
+[^github]: [https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group)
+
+# 2 The corpus
+
+As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
+The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*.
+This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on.
+The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts originating from various traditions, sects, and schools of jurisprudence.
+That desired breadth has yet to be achieved.
+The website currently has seventeen complete tafāsīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.
+
+## 2.1 The tafāsīr
+
+The following *tafāsīr* which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
 
@@
 
-# 2 The corpus
-
-As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
-The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*.
-This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on.
-The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts originating from various traditions, sects, and schools of jurisprudence.
-That desired breadth has yet to be achieved.
-The website currently has seventeen complete tafāsīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.
-
 # 3 Methodology
@@
 
-We ran a script that looked for duplicate texts and removed any repeated segments.
-Since we were not able to get word counts for specific verses, we decided to focus on the *sūra* or chapters of the Quran.
+After trying a number of different data formats for working with the corpus, we settled on importing it into relational database table which allowed us to perform queries either detailled or broad on it without necessarily having to write any logic.
+To give an example, the following SQL query would return *az-Zamaḫšarī*'s commentary on the fourth verse of the famous *sūrat al-iḫlāṣ* together with a simple character count:
+
+\singlespacing
+```{r, code=readLines('decoy.sql'), eval=FALSE}
+```
+\doublespacing
+
+We built a chain of queries first excluding duplicate texts and then any repeated segments.
+Appendix VI shows the full chain of queries which led to the CSV file that we then imported into a spreadsheet program to continue manually preparing it for network analysis.
+Because of the way most of the authors structure their commentary on the Quran, we were not able to get word counts for single verses, and so decided to focus on the *suwar* or chapters of the Quran.
 There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest.
@@
 We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
-The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.
+The relationship between the *mufassirūn* was visualized using Gephi[^gephi], a free/open-source program used for social network analysis.
 
-## 3.1 The Results
+[^gephi]: [https://gephi.org/](https://gephi.org/)
+
+## 3.1 The results
 
@@
 
-The data as described so far was run through the Gephi social network analysis program. The algorithm calculated four distinct groups, represented as colors in figure 1. They are as follows:
+Gephi's algorithm calculated four distinct groups, represented as colors in figure 1. They are as follows:
 
@@
 
-# Appendix
-
-Note on source code formatting: as this document was prepared using the `rmarkdown` package, consequently `knitr`'s built-in devices are being used to include our source code in the below appendices for reference.
-Unfortunately, it has not yet evolved to a point where it knows how to properly break-around longer lines as they often appear in source code files.
-The reader is kindly asked to open the source code files directly from [the GitHub repository where they are being kept](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group) if they wish to read them in detail.
-Towards that end, the appendix subheadings provide direct links to the files.
-
-Note on placement of appendix and references: another limitation of using Rmarkdown for scientific documents is the placement of references at the end of the document and nowhere else.
-This can only be worked around by use of a modified template file as described in [the Rmarkdown documentation's comment section](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
-Unfortunately, time constraints didn't allow creation of such a template for this document.
-
-```{r, echo=FALSE}
-library(knitr)
-opts_chunk$set(tidy.opts = list(width.cutoff=60, indent=2), tidy=TRUE)
-```
-
-## I Script [`01_retrieval/download.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/download.r)
-
-```{r, code=readLines('../01_retrieval/download.r'), eval=FALSE}
-```
-
-## II Script [`01_retrieval/extract.r`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/extract.r)
-
-```{r, code=readLines('../01_retrieval/extract.r'), eval=FALSE}
-```
-
-## III Script [`01_retrieval/process.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/process.rb)
-
-```{ruby, code=readLines('../01_retrieval/process.rb'), eval=FALSE}
-```
-
-## IV Script [`01_retrieval/convert.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/01_retrieval/convert.rb)
-
-```{ruby, code=readLines('../01_retrieval/convert.rb'), eval=FALSE}
-```
-
-## V Script [`02_analysis/wordcount_by_author.rb`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_by_author.rb)
-
-```{ruby, code=readLines('../02_analysis/wordcount_by_author.rb'), eval=FALSE}
-```
-
-## VI Query [`02_analysis/wordcount_whole_corpus.sql`](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group/02_analysis/wordcount_whole_corpus.sql)
-
-```{sql, code=readLines('../02_analysis/wordcount_whole_corpus.sql'), eval=FALSE}
-```
 # 4 References
 
-TODO: Keep moving them into Biblatex file, keep referencing properly in the text.
-
-"Al-Suyuti." Encyclopedia Britannica Online. May 16, 2007. Accessed December 1, 2016. https://www.britannica.com/biography/al-Suyuti.
-
-Bastian M., Heymann S., Jacomy M. (2009). Gephi: an open source software for exploring and manipulating networks. International AAAI Conference on Weblogs and Social Media
-
-Delfina Serrano Ruano, “al-Qurṭubī”, in: Encyclopaedia of the Qurʾān, General Editor: Jane Dammen McAuliffe, Georgetown University, Washington DC. Retrieved From http://www.brillonline.com
-
-Jackson, Sherman A(1996). Islamic law and the state: the constitutional jurisprudence of Shihāb al-Dīn al-Qarāfī. Leiden: E.J. Brill, 1996.
-
-Jaffer, Tariq (2015). Razi: Master of Qur'anic Interpretation and Theological Reasoning. New York, NY: Oxford University Press.
-
-"Liste des compagnies aériennes par pays." (2011) Wikipedia. Accessed December 1, 2016. https://fr.wikipedia.org/wiki/Liste_des_compagnies_a%C3%A9riennes_par_pays.
-
-Meri, Josef W., ed. (2005). "Suyuti, Al-, 'Abd al-Rahman". Medieval Islamic Civilization: An Encyclopedia. Routledge. pp. 784–786.
-
-Poonawala, I., Wensinck, A.J.
-and Heffening, W., “al-Nasafī”, in: Encyclopaedia of Islam, Second Edition, Edited by: P.
-Bearman, Th.
-Bianquis, C.E.
-Bosworth, E.
-van Donzel, W.P.
-Heinrichs.
-Retrieved from http://www.brillonline.com
-
-Sharif , M M. "Al-MĀWARDĪ." Encyclopaedia of Islam, Second Edition1, no. 3 (August 8, 2002). Accessed December 1, 2016. doi:10.1163/1573-3912_islam_com_0713.
-
-Wheeler, Brannon M. Prophets in the Quran: an introduction to the Quran and Muslim exegesis. London: Continuum, 2002.
-pg 337
-
-Zahoor, A., Dr. "Al-Mawardi, 972-1058 C.E." Al-Mawardi, 972-1058 C.E. January 15, 1998. Accessed December 1, 2016. http://www.unhas.ac.id/rhiza/arsip/saintis/mawardi.html.
+\singlespacing

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Fixed a ref. Changed font size, looks more readable to me that way.

@@
 toc: no
-fontsize: 11pt
+fontsize: 12pt
 lang: en

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Another paragraph transliterated and references added.

@@
 The transliteration system used is that of the German Oriental Society[^dmg_url].
-We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names); for the inconsistencies that remain (i.e., vowelisation was sometimes added where it helps the flow of pronounciation) we ask the reader's digression.
-With regards to diphtong phonemes we have opted towards the variant employing the combination of one consonantal and one vowel representation which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
-Proper names were translterated starting with capital letters only at the beginning of a sentence or if they are a person's or a place's name.
-Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if part of a group of other Arabic words.
+We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names); for the inconsistencies (i.e., vowelisation was sometimes added where it helps the flow of pronounciation, etc.) that remain we ask the reader's digression.
+As regards to diphtongs we have opted towards the variant employing the combination of consonant-plus-vowel which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
+Proper names were transliterated starting with capital letters only at the beginning of a sentence or if they are a person's or a place's name.
+Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if belonging to a group of other Arabic words.
 
@@
 
-TODO: DMGize, mark citations
-
 The last cluster of our analysis resulted in a predictable grouping of exegetes.
@@
 Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
-Amongst the four authors in this cluster three were from the school of šāfiʿī and one from the school of ḥanafī.
+Amongst the four authors in this cluster three were from the school of *aš-šāfiʿī* and one from the school of *al-ḥanafī*.
+
+*Al-Māwardī* was an Islamic jurist born in Basra, Iraq during 364AH (@ei_almawardi).
+During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
+The cities where *al-Māwardī* lived were known to be hubs of the *muʿtazila* school of thought, so some found it peculiar that the chief *qādī* of Baghdad (known hub of *muʿtazila* jurisprudence) was in fact associated with the šāfiʿī school of thought.
+He was later condemned for his *muʿtazila* sympathies.
+*Al-Māwardī* was known for his works in islamic legal principles, in fact in 429 AH the caliph *al-Qādir* summoned four jurists from each school of jurisprudence to write a legal epitome.
+(@ei_almawardi) *Al-Māwardī* was chosen to represent the school of šāfiʿī.
+Amongst the four jurists the Caliph favored *al-Māwardī* and appointed him chief Imam.
+(@ei_almawardi)
+
+Along with the school of jurisprudence a common factor amongst most of the authors was their interest in or relation to Islamic law.
 
@@
 
-Al–Mawardi was an Islamic jurist born in Basra, Iraq during 364AH (Sharif, 2002).
-During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
-The cities where al-mawari lived where known to be hubs of the Mu'tazaila school of thought, so some found it peculiar that the chief qadi of Baghdad (known hub of Mu'tazaila jurisprudence) was in fact associated with the šāfiʿī school of thought.
-He was later condemned for his *muʿtazila* sympathies.
-Al-Mawardi was known for his works in islamic legal principles, in fact in 429 AH the caliph Al-Qadir summoned four jurist from each school of jurisprudence to write a legal epitome.(Sharif, 2002) Al-Mawardi was chosen to represent the school of šāfiʿī.
-Amongst the four jurist the Caliph favored Al-Mawardi and appointed chief imam.
-(Sharif, 2002) Along with the school of jurisprudence a common factor amongst most of the authors was their interest or relation in Islamic law.
-
-TODO: DMGize, mark citations
-
-Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and Al–Mawardi.
+Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and *al-Māwardī*.
 During his time he was the leading authority in the šāfiʿī Jurisprudence and most famous for his interpretations of Islamic legal principles.
@@
 In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt.
-(Salahi) Like Al-Mawardi, Al- Salam was a world renowned scholar of fatwas.
-Al-salam was so respected, islamic jurist like al-Hafiz al-Mundhiri stopped giving fatwas stating "It does not behove any jurist to give a fatwa where Izz al-Din(Ibn 'Abd al-Salam) happens to be present."(Salahi) Both Ibn 'Abd al-Salam and Al-Mawardi were highly respected scholars of their time especially in regards to islamic law.
+(Salahi) Like *al-Māwardī*, Al- Salam was a world renowned scholar of fatwas.
+Al-salam was so respected, islamic jurist like al-Hafiz al-Mundhiri stopped giving fatwas stating "It does not behove any jurist to give a fatwa where Izz al-Din(Ibn 'Abd al-Salam) happens to be present."(Salahi) Both Ibn 'Abd al-Salam and *al-Māwardī* were highly respected scholars of their time especially in regards to islamic law.
 Both authors were advisors to their respected islamic governments of their time,(Jackson, 1996) another factor which may have attributed to the groups of these authors in the same cluster.
@@
 He was acknowledged as one of the more recent authority of the šāfiʿī school whose degree of ijthad was accepted by most(Meri,2005).
-Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and Al-Mawardi.
+Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and *al-Māwardī*.
 Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Finishing transliteration and citation references.

@@
 
-How has Islamic interpretation of the Quran changed over time?
+How has islamic interpretation of the Quran changed over time?
 Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time?
 Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another?
-Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration?
+Is doctrinal affiliation the primary factor in a *mufassir* (islamic exegete) giving a section of the Quran more consideration?
 To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format.
@@
 The transliteration system used is that of the German Oriental Society[^dmg_url].
-We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names); for the inconsistencies (i.e., vowelisation was sometimes added where it helps the flow of pronounciation, etc.) that remain we ask the reader's digression.
-As regards to diphtongs we have opted towards the variant employing the combination of consonant-plus-vowel which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
+We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names).
+For the inconsistencies that remain[^inconsistencies] we ask the reader's digression.
+As regards diphtongs we have opted towards the variant employing the combination of consonant plus vowel which we feel best evokes a "closer-to-correct" pronounciation in readers not trained in Arabic.
 Proper names were transliterated starting with capital letters only at the beginning of a sentence or if they are a person's or a place's name.
@@
 
+[^inconsistencies]: Mostly, vowelisation was sometimes added where it helps the flow of pronounciation.
+
 ## 1.2 A technical note regarding this document
@@
 
-[^github]: [https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group)
+[^github]: [https://github.com/islamicate-DH/hw/tree/master/tafaseer_group](https://github.com/islamicate-DH/hw/tree/master/tafaseer_group)
 
@@
 
-As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
+As part of an effort to make islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
 The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*.
@@
 * *tafsīr al-qurʾān* by *al-Fayrūzābādī*
-* *tafsīr al-qurʾān* by *Ibn ʿAbdi-s-Salām*
+* *tafsīr al-qurʾān* by *Ibn ʿAbd as-Salām*
 * *tafsīr al-qurʾān al-karīm* by *Ibn Kaṯīr*
@@
 3. Purple: *ar-Rāzī* (d. 606 AH), *al-Fayrūzābādī* (d. 817 AH), *al-Qurṭubī* (d. 671 AH), *al-Ḫāzin* (d. 741 AH), and *Abū Ḥayyān* (d. 754 AH)
-4. Orange: *al-Maḥallī* (d. 864 AH) and *as-Suyūṭī* (d. 911 AH), *as-Samarqandī* (d. 375 AH), *al-Māwardī* (d. 450 AH), and *Ibn ʿAbdi-s-Salām* (d. 660 AH)
+4. Orange: *al-Maḥallī* (d. 864 AH) and *as-Suyūṭī* (d. 911 AH), *as-Samarqandī* (d. 375 AH), *al-Māwardī* (d. 450 AH), and *Ibn ʿAbd as-Salām* (d. 660 AH)
 
@@
 *Aṭ-Ṭabarī* saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
-*Al-Baġawī* emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
+*Al-Baġawī* emphasized the importance of purity in islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
 *Ḥanbalī* adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of *ismaʿīlī* Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
@@
 
-*Al-Māwardī* was an Islamic jurist born in Basra, Iraq during 364AH (@ei_almawardi).
+*Al-Māwardī* was an islamic jurist born in Basra, Iraq during 364 AH (@ei_almawardi).
 During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
@@
 He was later condemned for his *muʿtazila* sympathies.
-*Al-Māwardī* was known for his works in islamic legal principles, in fact in 429 AH the caliph *al-Qādir* summoned four jurists from each school of jurisprudence to write a legal epitome.
-(@ei_almawardi) *Al-Māwardī* was chosen to represent the school of šāfiʿī.
-Amongst the four jurists the Caliph favored *al-Māwardī* and appointed him chief Imam.
-(@ei_almawardi)
+*Al-Māwardī* was known for his works in islamic legal principles, in fact in 429 AH the caliph *al-Qādir* summoned four jurists from each school of jurisprudence to write a legal epitome (@ei_almawardi).
+*Al-Māwardī* was chosen to represent the school of šāfiʿī.
+Amongst the four jurists the Caliph favored *al-Māwardī* and appointed him chief Imam (@ei_almawardi).
 
-Along with the school of jurisprudence a common factor amongst most of the authors was their interest in or relation to Islamic law.
+Along with the school of jurisprudence a common factor amongst most of the authors was their interest in or relation to islamic law.
 
-TODO: DMGize, mark citations
+3.2 Remarks on noteworthy authors of works in the corpus
 
-Ibn 'Abd al-Salam was born in Damascus in year 577AH(Salahi) much after Abu al-Layth Al Samarqandi and *al-Māwardī*.
-During his time he was the leading authority in the šāfiʿī Jurisprudence and most famous for his interpretations of Islamic legal principles.
-Unlike al mawari ,Abd al-Salam was known to be defiant of customs he deemed “unsanctioned”.
-He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus As-Salih Ismail.(Jackson, 1996) This condemning led to his imprisonment and eventual emigration to Cairo, Egypt.
-In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt.
-(Salahi) Like *al-Māwardī*, Al- Salam was a world renowned scholar of fatwas.
-Al-salam was so respected, islamic jurist like al-Hafiz al-Mundhiri stopped giving fatwas stating "It does not behove any jurist to give a fatwa where Izz al-Din(Ibn 'Abd al-Salam) happens to be present."(Salahi) Both Ibn 'Abd al-Salam and *al-Māwardī* were highly respected scholars of their time especially in regards to islamic law.
-Both authors were advisors to their respected islamic governments of their time,(Jackson, 1996) another factor which may have attributed to the groups of these authors in the same cluster.
+*ʿIzz ad-Dīn ibn ʿAbd as-Salām* was born in Damascus in the year 577 AH (@salahi2016), long after *as-Samarqandī* and *al-Māwardī*.
+During his time he was the leading authority in the *šāfiʿī* jurisprudence and most famous for his interpretations of islamic legal principles.
+Unlike *al-Māwardī*, *ʿAbd as-Salām* was known to be defiant of customs he deemed "unsanctioned".
+He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus, aṣ-Ṣāliḥ ʾIsmaʿīl (@jackson1996).
+This condemning led to his imprisonment and eventual emigration to Cairo, Egypt.
+In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt (@salahi2016).
+Like *al-Māwardī*, *as-Salām* was a world renowned scholar of *fatāwa* (sg.
+fatwa, islamic legal opinion).
+Indeed, *as-Salām* was so respected, islamic jurists like *al-Ḥāfiẓ al-Munḏirī* stopped giving *fatāwa* stating that "[i]t does not behove any jurist to give a *fatwa* where *ʿIzz ad-Dīn* [*Ibn ʿAbd as-Salām*] happens to be present" (@salahi2016).
+Both *Ibn ʿAbd as-Salām* and *al-Māwardī* were highly respected scholars of their time especially in regards to islamic law.
+Both authors were advisors to respected islamic governments of their time (@jackson1996), another factor which may have attributed to the grouping of these authors in the same cluster.
 
-TODO: DMGize, mark citations
+*Ǧalāl ad-Dīn as-Suyūṭī* was born in Cario, Eygpt in the year 849 AH (@eb_alsuyuti) making his work the most recent amongst the cluster.
+Like most authors in the cluster he was an islamic jurist from the school of *aš-Šāfiʿī*.
+He was acknowledged as one of the more recent authorities of the *šāfiʿī* school whose degree of *iǧtihād* was accepted by most (@mic_alsuyuti).
+*As-Suyūṭī* lacked a particular interest in islamic law and was not known to be a head advisor for any islamic governments like both *Ibn ʿAbd as-Salām* and *al-Māwardī*.
+Although his father being a judge of an islamic state may have influenced any emphasis on (islamic) law within his writings and thus placing him within this cluster (@eb_alsuyuti).
+Unlike the other authors, *as-Suyūṭī* also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from the *šāfiʿī* school of thought.
+*As-Suyūṭī*'s interest in the *ḥanafī* jurisprudence may account for the inclusion of *as-Samarqandī* in the cluster.
 
-Jalal al-Din al-Suyuti was born in Cario, Eygpt in the year 849AH (al-Suyuti, 2007) making his work the most recent amongst the cluster.
-Like most authors in the cluster he was a islamic jurist from the school of šāfiʿī.
-He was acknowledged as one of the more recent authority of the šāfiʿī school whose degree of ijthad was accepted by most(Meri,2005).
-Jalal al-Din al-Suyuti lacked a particular interest in islamic law and was not known to be a head advisor for any Islamic governments like both Ibn 'Abd al-Salam and *al-Māwardī*.
-Although his father being a judge of a islamic state may have influenced any emphasis on law(islamic) within his writings and thus placing him within this cluster.(al-suyuti,2007) Unlike the other authors, al-Suyuti also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from šāfiʿī school of thought.
-Al-Suyuti's interest in the *ḥanafī* jurisprudence may account for the inclusion of Abu al-Layth Al Samarqandi in our cluster.
+*Abū al-Layṯ as-Samarqandī*, author of *baḥr al-ʿulūm* was the single author in the cluster from the school of *al-Ḥanafī*.
+Apart from his jurisprudence another outlying factor for *as-Samarqandī* was his geographical location and time period.
+He was born in Afghanistan during 373 AH making him the oldest exegete in this cluster (@wheeler2002 [p.
+337]).
+Since his worked dated back so far we were unable to find much information in regards to his lifestyle or any other factors that may have attributed to his placing in this cluster.
+We were however able to compile a few specific features of his exegesis.
+In his work on the Quran *as-Samarqandī* was known to relate the stories of *ṣaḥāba* and other *ḥadīṯ* from people not proven to be entirely reliable.
+He was also known for his lack of interest in the various methods of recitation (*qirāʾāt*; @wikipedia_listofairlinecodes).
+Unfortunately, due to lack of information on *as-Samarqandī* we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
 
-TODO: DMGize, mark citations
-
-Abu al-Layth al-Samarqandi author of Bahr Ul ‘Ulum was the single author in the cluster from the school of ḥanafī.
-Apart from his jurisprudence another outlying factor for al-Samaraqandi was his geographical location and time period.
-He was born in Afghanistan during 373AH making him the oldest exegete in this cluster.
-(wheeler, 2002) Since his worked dated back so far we were unable to find much information in regards to his lifestyle or any other factors that may have attributed to his placing in this cluster although, however we were able to compile a few specific features of his exegesis.
-In his work of the Quran al-samarqandi was known to relate the stories of sahabah and other hadiths from people not proven to be 100% reliable.
-He was also known for his lack of interest in the various methods of recitation (Qira'at).(“Liste..” 2002) Unfortunately, due to lack of information on Al Samarqandi we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
-
-TODO: DMGize, mark citations
+4 Conclusion
 
 From the results of the study, we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of the paper (chronology, geography, dogma).
-However, we believe that examination of surah and ayah preference from Quranic exegetes deserves further exploration.
+However, we believe that examination of *sūra* and *āyā* preference from Quranic exegetes deserves further exploration.
 
-# 4 References
+# 5 References
 

### 2016-12-20 tafaseer_group/03_results/paper.rmd
final version?

@@
 
-The transliteration system used is that of the German Oriental Society[^dmg_url].
+The transliteration system used is that of the German Oriental Society[^dmg].
 We have tried to be consistent in our transliteration of Arabic words (and sometimes Persian names).
@@
 Words that have found their way into English[^englishwords], and which the reader can be assumed to be familiar with, were only transliterated if belonging to a group of other Arabic words.
-
-[^dmg_url]: [http://www.dmg-web.de/](http://www.dmg-web.de/)
 
@@
 
-The present document was prepared using the `rmarkdown` package and consequently `knitr`'s built-in devices are being used to include the source code relevant to this study in the appendix.
-Unfortunately, the underlying libraries have not yet evolved to a point where they knows how to properly break-around longer lines as they often appear in source code files.
+The present document was prepared using the `rmarkdown`[^rmarkdown] package and consequently `knitr`'s[^knitr] built-in devices are being used to include the source code relevant to this study in the appendix.
+Unfortunately, the underlying libraries have not yet evolved to a point where they know how to properly break-around longer lines as they often appear in source code files.
 The reader is kindly asked to open the source code files directly from the GitHub repository where they are being kept[^github] if she wishes to read them in detail.
 Towards that end, the appendix subheadings provide direct links to the respective files displayed beneath them.
+
+[^rmarkdown]: [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/)
+
+[^knitr]: [http://yihui.name/knitr/](http://yihui.name/knitr/)
 
@@
 Because of the way most of the authors structure their commentary on the Quran, we were not able to get word counts for single verses, and so decided to focus on the *suwar* or chapters of the Quran.
-There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest.
+There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *suwar*, from longest to shortest.
 We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting.
 We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
+
 The relationship between the *mufassirūn* was visualized using Gephi[^gephi], a free/open-source program used for social network analysis.
+Each writer is represented as a "node" on the graph.
+An "edge" is a connection between nodes which for our research is a *sūra* from the list of twenty-five that is shared by writers.
+A connection is weighted for each additional, shared *sūra* so that the connection between writers who share numerous *suwar* is stronger than the connection between those who share few.
+Gephi has a modularity function that defines sub-networks which we believed could show which of the writers of the corpus were similar in the manner that they gave certain *suwar* more attention.
+What resulted from the calculation was the clustering of the *mufassirūn* into four groups.
 
@@
 The primary characteristic that unified these authors was their choice of school of jurisprudence.
-Although these exegetes were all from different time periods and, for the most part, varying geographical locations the analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
-Amongst the four authors in this cluster three were from the school of *aš-šāfiʿī* and one from the school of *al-ḥanafī*.
+These exegetes were all from different time periods and, for the most part, varying geographical locations yet still their analogous school of thought when approaching the interpretations of the Quran was similar enough to differentiate this group from the rest of our corpus.
+Amongst the four authors in this cluster three were from the school of *aš-Šāfiʿī* and one from the school of *al-Ḥanafī*.
 
 *Al-Māwardī* was an islamic jurist born in Basra, Iraq during 364 AH (@ei_almawardi).
-During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Iman of Baghdad (Zahoor, 1998) .
-The cities where *al-Māwardī* lived were known to be hubs of the *muʿtazila* school of thought, so some found it peculiar that the chief *qādī* of Baghdad (known hub of *muʿtazila* jurisprudence) was in fact associated with the šāfiʿī school of thought.
+During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Imam of Baghdad (@zahoor1998) .
+The city where *al-Māwardī* lived was known to be a hub of the *muʿtazila* school of thought, so some found it peculiar that the chief Imam of Baghdad (known hub of *muʿtazila* jurisprudence) was in fact associated with the šāfiʿī school of thought.
 He was later condemned for his *muʿtazila* sympathies.
@@
 
-Along with the school of jurisprudence a common factor amongst most of the authors was their interest in or relation to islamic law.
+Along with school of jurisprudence, a common factor amongst most of the authors was their interest in or relation to islamic law.
 
-3.2 Remarks on noteworthy authors of works in the corpus
+## 3.2 Remarks on noteworthy authors of works in the corpus after network analysis
 
@@
 In his work on the Quran *as-Samarqandī* was known to relate the stories of *ṣaḥāba* and other *ḥadīṯ* from people not proven to be entirely reliable.
-He was also known for his lack of interest in the various methods of recitation (*qirāʾāt*; @wikipedia_listofairlinecodes).
+He was also known for his lack of interest in the various *qirāʾāt*, the methods of recitation of the Quran (@wikipedia_alsamarqandi)[^weirdness].
 Unfortunately, due to lack of information on *as-Samarqandī* we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
 
-4 Conclusion
+[^weirdness]: The quoted Wikipedia article does not contain the information on *Abū al-Layṯ as-Samarqandī* stated here.
+Unfortunately, the originally quoted article could not be found again before conclusion of this paper.
+May the citation as it stands serve as a starting point as to where the information may be obtained by any who may need to access it.
+The editor.
+
+# 4 Conclusion
 
 From the results of the study, we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of the paper (chronology, geography, dogma).
-However, we believe that examination of *sūra* and *āyā* preference from Quranic exegetes deserves further exploration.
+It is our contention that examining commentaries that are able to be divided up at the verse-level should yield clearer, more consistent clusters.
+There was a surprisingly large degree of overlap among the lists of top twenty-five *suwar*.
+Shorter *suwar* may require more commentary simply because their laconic nature demands contextualizing and therefore their placement at the top of the lists reveals little about the attention *mufassirūn* gave to certain sections of the Quran.
+What this research did was attempt to explore  a new method of charting the relationship of Quranic scholars that relies on an impartial, distant examination of *tafāsīr* that traditional categorization--according to sect or school of jurisprudence--may lack.
+The results were not as conclusive as we had hoped, however, we believe that examination of *sūra* and *āyā* preferences of Quranic exegetes deserves further exploration.
 

### 2016-12-20 tafaseer_group/03_results/paper.rmd
bah

@@
 
-Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the tafsir that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*.
+Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the *tafsīr* that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*.
 It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*.

### 2016-12-20 tafaseer_group/03_results/paper.rmd
Last round of editing finished.

@@
 
-How has islamic interpretation of the Quran changed over time?
+How has Islamic interpretation of the Quran changed over time?
 Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time?
 Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another?
-Is doctrinal affiliation the primary factor in a *mufassir* (islamic exegete) giving a section of the Quran more consideration?
+Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration?
 To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format.
@@
 
-[^github]: [https://github.com/islamicate-DH/hw/tree/master/tafaseer_group](https://github.com/islamicate-DH/hw/tree/master/tafaseer_group)
+[^github]: [https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group](https://github.com/Islamicate-DH/hw/tree/master/tafaseer_group)
 
@@
 
-As part of an effort to make islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
+As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*.
 The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*.
@@
 
-The following *tafāsīr* which ended up being the subject of this document are listed below. Short remarks on each of their authors' biographies will follow.
+The following *tafāsīr* which ended up being the subject of the present paper are listed below. Short remarks on some of their authors' biographies will follow in section 3.2.
 
@@
 Importance might not necessarily mean that the *mufassir* had an increased affinity for the values or instructions espoused in the verse.
-A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the Muslim layman and therefore devoted more writing to explication and contextualizing.
+A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the layman Muslim and therefore devoted more writing to explication and contextualizing.
 
@@
 The problem was that most of the writers alternated between writing about singles verses and writing about groups of consecutive verses that dealt with a single narrative or theme.
-If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website.
-When the script to download the tafāsīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse.
+If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when any one of those verses were selected on the website.
+When the script to download the *tafāsīr* was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse.
 Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem.
@@
 
-After trying a number of different data formats for working with the corpus, we settled on importing it into relational database table which allowed us to perform queries either detailled or broad on it without necessarily having to write any logic.
+After trying a number of different data formats for working with the corpus, we settled on importing it into a relational database table which enabled us to perform queries either detailled or broad on it without necessarily having to write any logic.
 To give an example, the following SQL query would return *az-Zamaḫšarī*'s commentary on the fourth verse of the famous *sūrat al-iḫlāṣ* together with a simple character count:
@@
 
-We built a chain of queries first excluding duplicate texts and then any repeated segments.
-Appendix VI shows the full chain of queries which led to the CSV file that we then imported into a spreadsheet program to continue manually preparing it for network analysis.
-Because of the way most of the authors structure their commentary on the Quran, we were not able to get word counts for single verses, and so decided to focus on the *suwar* or chapters of the Quran.
+We built a chain of queries first excluding duplicate texts and subsequently any repeat segments.
+Appendix VI shows the full chain of queries which led to the CSV file that was then imported into a spreadsheet program to continue manually preparing it for network analysis.
+Because of the way most of the authors structure their commentary on the Quran, we were not able to get word counts for single verses/*āyāt*, and so decided to focus on the chapters/*suwar*.
 There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *suwar*, from longest to shortest.
 We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting.
-We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two.
+We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *suwar* among the writers of the corpus ranged from twelve to twenty-two.
 
@@
 The unifying characteristic for the exegetes of the first cluster is their reputation as traditionalists.
-*Aṭ-Ṭabarī* saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on Hadith in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
-*Al-Baġawī* emphasized the importance of purity in islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
+*Aṭ-Ṭabarī* saw his method of *tafsīr bi-l-maṯūr*, or exclusive reliance on *ḥadīṯ* (accounts on the life of the prophet Muḥammad) in matters of Quranic interpretation, as essential to avoid the introduction of *bidʿa* or heretical innovation (@bauer2013).
+*Al-Baġawī* emphasized the importance of purity in Islamic doctrine and worked to exclude teachings that he believed could not be properly attributed to Muḥammad or the *ṣaḥāba*, the companions of Muḥammad (@ei_albaghawi).
 *Ḥanbalī* adherent *Ibnu-l-Ǧawzī* campaigned against the Shia in Iraq and authored a paean[^paean] celebrating the end of *ismaʿīlī* Fatimid rule in Egypt and the accession of a Sunni, *Ṣalāḥ ad-Dīn*, to power (@mallett).
 *Ibn ʿAṭīya*'s exegesis received praise from *Ibn Taimīya*, the intellectual forefather of movements that are frequently labeled as Salafist, for its adherence to orthodoxy (@salahi2002).
-The inclusion of *Ibn Taimīya*'s student *Ibn Kaṯīr* can be attributed to either his conservative leanings—he penned a defense of armed Jihad against neighboring non-Muslim states (@ei_ibnkathir)—or to his *tafsīr* being, as some scholars have observed, a summarized version of *aṭ-Ṭabarī* (@mcauliffe1991).
+The inclusion of *Ibn Taimīya*'s student *Ibn Kaṯīr* can be attributed to either his conservative leanings—he penned a defense of armed jihad against neighboring non-Muslim states (@ei_ibnkathir)—or to his *tafsīr* being, as some scholars have observed, a summarized version of *aṭ-Ṭabarī* (@mcauliffe1991).
 
@@
 *Abū Ḥayyān* (@ei_abuhayyan) and *al-Qurṭubī* were both born in Muslim Spain and ultimately settled in Egypt (Ruano, n.d.).
-Al-Khazin lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (@ei_alfiruzabadi).
+*Al-Ḫāzin* lived in Syria which also was briefly the home of Persian-born *al-Fayrūzābādī* who also spent his life in Jerusalem, Mecca, and Yemen (@ei_alfiruzabadi).
 *ar-Rāzī* lived in what is now Iran and Afghanistan (@mcauliffe1991).
@@
 
-*Al-Māwardī* was an islamic jurist born in Basra, Iraq during 364 AH (@ei_almawardi).
-During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Imam of Baghdad (@zahoor1998) .
-The city where *al-Māwardī* lived was known to be a hub of the *muʿtazila* school of thought, so some found it peculiar that the chief Imam of Baghdad (known hub of *muʿtazila* jurisprudence) was in fact associated with the šāfiʿī school of thought.
-He was later condemned for his *muʿtazila* sympathies.
-*Al-Māwardī* was known for his works in islamic legal principles, in fact in 429 AH the caliph *al-Qādir* summoned four jurists from each school of jurisprudence to write a legal epitome (@ei_almawardi).
-*Al-Māwardī* was chosen to represent the school of šāfiʿī.
-Amongst the four jurists the Caliph favored *al-Māwardī* and appointed him chief Imam (@ei_almawardi).
-
-Along with school of jurisprudence, a common factor amongst most of the authors was their interest in or relation to islamic law.
+Along with school of jurisprudence, a common factor amongst most of the authors was their interest in or relation to Islamic Law.
 
@@
 
+*Al-Māwardī* was an Islamic jurist born in Basra, Iraq during 364 AH (@ei_almawardi).
+During his time he was considered a high profile figure appointed with various significant responsibilities, including serving as a diplomat for the caliphate and eventually appointed chief Imam of Baghdad (@zahoor1998) .
+The city where *al-Māwardī* lived was known to be a hub of the *muʿtazila* school of thought, so some found it peculiar that its chief Imam was in fact associated with the šāfiʿī school of thought.
+He was later condemned for his *muʿtazila* sympathies.
+*Al-Māwardī* was known for his works in Islamic legal principles, in fact in 429 AH the caliph *al-Qādir* summoned four jurists from each school of jurisprudence to write a legal epitome (@ei_almawardi).
+*Al-Māwardī* was chosen to represent the school of *aš-Šāfiʿī*.
+Amongst the four jurists the Caliph favored *al-Māwardī* and appointed him chief Imam (@ei_almawardi).
+
 *ʿIzz ad-Dīn ibn ʿAbd as-Salām* was born in Damascus in the year 577 AH (@salahi2016), long after *as-Samarqandī* and *al-Māwardī*.
-During his time he was the leading authority in the *šāfiʿī* jurisprudence and most famous for his interpretations of islamic legal principles.
+During his time he was the leading authority in the *šāfiʿī* jurisprudence and most famous for his interpretations of Islamic legal principles.
 Unlike *al-Māwardī*, *ʿAbd as-Salām* was known to be defiant of customs he deemed "unsanctioned".
-He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus, aṣ-Ṣāliḥ ʾIsmaʿīl (@jackson1996).
+He even went as far as condemning those who follow these unsanctioned customs regardless of status; most notably the ruler of Damascus, *aṣ-Ṣāliḥ ʾIsmaʿīl* (@jackson1996).
 This condemning led to his imprisonment and eventual emigration to Cairo, Egypt.
-In Cairo he was credited as the first jurist to teach Quranic commentary in Egypt (@salahi2016).
+There, he was credited as the first jurist to teach Quranic commentary in Egypt (@salahi2016).
 Like *al-Māwardī*, *as-Salām* was a world renowned scholar of *fatāwa* (sg.
-fatwa, islamic legal opinion).
-Indeed, *as-Salām* was so respected, islamic jurists like *al-Ḥāfiẓ al-Munḏirī* stopped giving *fatāwa* stating that "[i]t does not behove any jurist to give a *fatwa* where *ʿIzz ad-Dīn* [*Ibn ʿAbd as-Salām*] happens to be present" (@salahi2016).
-Both *Ibn ʿAbd as-Salām* and *al-Māwardī* were highly respected scholars of their time especially in regards to islamic law.
-Both authors were advisors to respected islamic governments of their time (@jackson1996), another factor which may have attributed to the grouping of these authors in the same cluster.
+*fatwa*, a document of legal opinion in Islamic Law).
+Indeed, *as-Salām* was so respected, Islamic jurists like *al-Ḥāfiẓ al-Munḏirī* stopped giving *fatāwa* stating that "[i]t does not behove any jurist to give a *fatwa* where *ʿIzz ad-Dīn* [*Ibn ʿAbd as-Salām*] happens to be present" (@salahi2016).
+Both *Ibn ʿAbd as-Salām* and *al-Māwardī* were highly respected scholars of their time especially in regards to Islamic Law.
+Both authors were advisors to respected Islamic governments of their time (@jackson1996), another factor which may have attributed to the grouping of these authors in the same cluster.
 
-*Ǧalāl ad-Dīn as-Suyūṭī* was born in Cario, Eygpt in the year 849 AH (@eb_alsuyuti) making his work the most recent amongst the cluster.
-Like most authors in the cluster he was an islamic jurist from the school of *aš-Šāfiʿī*.
-He was acknowledged as one of the more recent authorities of the *šāfiʿī* school whose degree of *iǧtihād* was accepted by most (@mic_alsuyuti).
-*As-Suyūṭī* lacked a particular interest in islamic law and was not known to be a head advisor for any islamic governments like both *Ibn ʿAbd as-Salām* and *al-Māwardī*.
-Although his father being a judge of an islamic state may have influenced any emphasis on (islamic) law within his writings and thus placing him within this cluster (@eb_alsuyuti).
+Where *ʿAbd as-Salām* died, much later *Ǧalāl ad-Dīn as-Suyūṭī* was born in the year 849 AH (@eb_alsuyuti), making his work the most recent here mentioned.
+Like most authors in the cluster he was an Islamic jurist from the school of *aš-Šāfiʿī*.
+He was acknowledged as one of the more recent authorities of the *šāfiʿī* school whose degree of *iǧtihād* was "accepted by most" (@mic_alsuyuti).
+*As-Suyūṭī* lacked a particular interest in Islamic Law and was not known to be a head advisor for any Islamic government like both *Ibn ʿAbd as-Salām* and *al-Māwardī* had been.
+Although his father having been a judge of an Islamic state may have influenced any emphasis on the (Islamic) law within his writings and thus placing him within this cluster (@eb_alsuyuti).
 Unlike the other authors, *as-Suyūṭī* also studied the *ḥanafī* school of jurisprudence and was tutored by a Sufi, though his work drew primarily from the *šāfiʿī* school of thought.
@@
 
-*Abū al-Layṯ as-Samarqandī*, author of *baḥr al-ʿulūm* was the single author in the cluster from the school of *al-Ḥanafī*.
+*Abu-l-Layṯ as-Samarqandī*, author of *baḥr al-ʿulūm* was the single author in the cluster from the school of *al-Ḥanafī*.
 Apart from his jurisprudence another outlying factor for *as-Samarqandī* was his geographical location and time period.
@@
 337]).
-Since his worked dated back so far we were unable to find much information in regards to his lifestyle or any other factors that may have attributed to his placing in this cluster.
-We were however able to compile a few specific features of his exegesis.
-In his work on the Quran *as-Samarqandī* was known to relate the stories of *ṣaḥāba* and other *ḥadīṯ* from people not proven to be entirely reliable.
-He was also known for his lack of interest in the various *qirāʾāt*, the methods of recitation of the Quran (@wikipedia_alsamarqandi)[^weirdness].
-Unfortunately, due to lack of information on *as-Samarqandī* we were unable to pinpoint a specific factor that attributed to his grouping in this cluster, for now he remains an outlier.
-
-[^weirdness]: The quoted Wikipedia article does not contain the information on *Abū al-Layṯ as-Samarqandī* stated here.
-Unfortunately, the originally quoted article could not be found again before conclusion of this paper.
-May the citation as it stands serve as a starting point as to where the information may be obtained by any who may need to access it.
-The editor.
+Since his work dated back so far we were unable to find much information as regards his lifestyle or any other factors that may have attributed to his placing in this cluster.
+We were however able to compile a few specific features of his exegesis: in his work on the Quran, *as-Samarqandī* was known to relate the stories of *ṣaḥāba* and of other *ḥadīṯ* from people not proven to be entirely reliable.
+He was also known for his lack of interest in the various *qirāʾāt*, the methods of recitation of the Quran (@wpfr_tafsirsamarqandi).
+Unfortunately, due to lack of information on *as-Samarqandī* we were unable to pinpoint a specific factor that would explain his grouping in the fourth, or orange cluster.
+For the time being he remains an outlier.
 
@@
 
-From the results of the study, we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of the paper (chronology, geography, dogma).
+From the results of the study we cannot definitively state that focusing on certain aspects of the Quran is determined principally by any of the factors mentioned at the beginning of this paper (chronology, geography or dogma).
 It is our contention that examining commentaries that are able to be divided up at the verse-level should yield clearer, more consistent clusters.
@@
 Shorter *suwar* may require more commentary simply because their laconic nature demands contextualizing and therefore their placement at the top of the lists reveals little about the attention *mufassirūn* gave to certain sections of the Quran.
-What this research did was attempt to explore  a new method of charting the relationship of Quranic scholars that relies on an impartial, distant examination of *tafāsīr* that traditional categorization--according to sect or school of jurisprudence--may lack.
-The results were not as conclusive as we had hoped, however, we believe that examination of *sūra* and *āyā* preferences of Quranic exegetes deserves further exploration.
+What this research did was attempt to explore  a new method of charting the relationships of Quranic scholars that rely on an impartial, distant examination of *tafāsīr* that traditional categorization--according to sect or school of jurisprudence--may lack.
+The results were not as conclusive as we had hoped, however, we believe that examination of *sūra* and *āya* preferences of Quranic exegetes deserves further exploration.
 
